### 2024-02-11 outputs/replication/replication.qmd

---
title: "Replication for figures and graphs"
author: "Boxuan Yi, Ruoxian Wu"
format: pdf
---

```{r}
#| message: false
#| echo: false
# Install packages we need
install.packages('haven')
install.packages('dplyr')
install.packages('ggplot2')
install.packages('readr')
install.packages('here')
install.packages('janitor')
install.packages('knitr')
install.packages("kableExtra")
```

```{r}
#| message: false
#| echo: false
library(haven)
library(dplyr)
library(ggplot2)
library(readr)
library(here)
library(janitor)
library(knitr)
library(kableExtra)
```

```{r}
#| message: false
#| echo: false
# Read the dataset
main_clean <- read_dta(here("inputs/data/01_main_exp_clean.dta"))
follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean.dta"))
online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean.dta"))
```

```{r}
#| include: false
# Test
main_clean$condition2 |> unique()
```

```{r}
#| include: false
# Observations
total_rows <- nrow(main_clean)
c_rows <- sum(main_clean$condition2 == 0, na.rm = TRUE)
t_rows <- sum(main_clean$condition2 == 1, na.rm = TRUE)

# Age
total_age <- round(mean(main_clean$age, na.rm = TRUE), 2)
c_age <- round(mean(main_clean$age[main_clean$condition2 == 0], na.rm = TRUE), 2)
t_age <- round(mean(main_clean$age[main_clean$condition2 == 1], na.rm = TRUE), 2)
# Age standard deviation
total_age_sd <- paste0("(", round(sd(main_clean$age, na.rm = TRUE), 2), ")")
c_age_sd <- paste0("(", round(sd(main_clean$age[main_clean$condition2 == 0], na.rm = TRUE), 2), ")")
t_age_sd <- paste0("(", round(sd(main_clean$age[main_clean$condition2 == 1], na.rm = TRUE), 2), ")")

# Number of children
total_ch <- round(mean(main_clean$children, na.rm = TRUE), 2)
c_ch <- round(mean(main_clean$children[main_clean$condition2 == 0], na.rm = TRUE), 2)
t_ch <- round(mean(main_clean$children[main_clean$condition2 == 1], na.rm = TRUE), 2)
# Number of children standard deviation
total_ch_sd <- paste0("(", round(sd(main_clean$children, na.rm = TRUE), 2), ")")
c_ch_sd <- paste0("(", round(sd(main_clean$children[main_clean$condition2 == 0], na.rm = TRUE), 2), ")")
t_ch_sd <- paste0("(", round(sd(main_clean$children[main_clean$condition2 == 1], na.rm = TRUE), 2), ")")

# College Degree (%)
total_cd <- round(mean(main_clean$college_deg == 1, na.rm = TRUE) * 100, 2)
c_cd <- main_clean |> filter(condition2 == 0) |>
  summarise(c_cd = round(mean(college_deg == 1, na.rm = TRUE) * 100, 2)) |> pull(c_cd)
t_cd <- main_clean |> filter(condition2 == 1) |>
  summarise(t_cd = round(mean(college_deg == 1, na.rm = TRUE) * 100, 2)) |> pull(t_cd)

# Employed (%)
total_emp <- round((sum(main_clean$employed_now == 1, na.rm = TRUE) / total_rows) * 100, 2)
c_emp <- main_clean %>%
  filter(condition2 == 0) %>%
  summarise(c_emp = round(sum(employed_now == 1, na.rm = TRUE) / c_rows * 100, 2)) %>%
  pull(c_emp)
t_emp <- main_clean %>%
  filter(condition2 == 1) %>%
  summarise(t_emp = round(sum(employed_now == 1, na.rm = TRUE) / t_rows * 100, 2)) %>%
  pull(t_emp)

# Wife employed (%)
total_we <- round((sum(main_clean$employed_wife == 1, na.rm = TRUE) / total_rows) * 100, 2)
c_we <- main_clean %>%
  filter(condition2 == 0) %>%
  summarise(c_we = round(sum(employed_wife == 1, na.rm = TRUE) / c_rows * 100, 2)) %>%
  pull(c_we)
t_we <- main_clean %>%
  filter(condition2 == 1) %>%
  summarise(t_we = round(sum(employed_wife == 1, na.rm = TRUE) / t_rows * 100, 2)) %>%
  pull(t_we)

# Wife working outside the home (% retrospective follow-up)
c_wo <- follow_up_clean %>%
  filter(condition2 == 0) %>%
  filter(matched == 1) %>%
  summarise(c_wo = round(mean(employed_3mos_out_fl) * 100, 2)) %>%
  pull(c_wo)
t_wo <- follow_up_clean %>%
  filter(condition2 == 1) %>%
  filter(matched == 1) %>%
  summarise(t_wo = round(mean(employed_3mos_out_fl) * 100, 2)) %>%
  pull(t_wo)
total_wo <- follow_up_clean %>%
  filter(matched == 1) %>%
  summarise(total_wo = round(mean(employed_3mos_out_fl) * 100, 2)) %>%
  pull(total_wo)

# Other participants known (%)
total_kn <- round(mean(main_clean$num_know_per, na.rm = TRUE) * 100, 2)
c_kn <- main_clean %>%
  filter(condition2 == 0) %>%
  summarise(c_kn = round(mean(num_know_per, na.rm = TRUE) * 100, 2)) %>%
  pull(c_kn)
t_kn <- main_clean %>%
  filter(condition2 == 1) %>%
  summarise(t_kn = round(mean(num_know_per, na.rm = TRUE) * 100, 2)) %>%
  pull(t_kn)
# Other participants known standard deviation (%)
total_kn_sd <- paste0("(", round(sd(main_clean$num_know_per, na.rm = TRUE) * 100, 2), ")")
c_kn_sd <- paste0("(", round(sd(main_clean$num_know_per[main_clean$condition2 == 0], na.rm = TRUE) * 100, 2), ")")
t_kn_sd <- paste0("(", round(sd(main_clean$num_know_per[main_clean$condition2 == 1], na.rm = TRUE) * 100, 2), ")")

# Other participants with mutual friends (%)
total_mf <- round(mean(main_clean$num_mfs_per, na.rm = TRUE) * 100, 2)
c_mf <- main_clean %>%
  filter(condition2 == 0) %>%
  summarise(c_mf = round(mean(num_mfs_per, na.rm = TRUE) * 100, 2)) %>%
  pull(c_mf)
t_mf <- main_clean %>%
  filter(condition2 == 1) %>%
  summarise(t_mf = round(mean(num_mfs_per, na.rm = TRUE) * 100, 2)) %>%
  pull(t_mf)
# Other participants with mutual friends standard deviation (%)
total_mf_sd <- paste0("(", round(sd(main_clean$num_mfs_per, na.rm = TRUE) * 100, 2), ")")
c_mf_sd <- paste0("(", round(sd(main_clean$num_mfs_per[main_clean$condition2 == 0], na.rm = TRUE) * 100, 2), ")")
t_mf_sd <- paste0("(", round(sd(main_clean$num_mfs_per[main_clean$condition2 == 1], na.rm = TRUE) * 100, 2), ")")
```

```{r}
#| include: false
# Assign groups
total_group <- c(total_rows, total_age, total_age_sd, total_ch, total_ch_sd, total_cd, total_emp, total_we, total_wo, total_kn, total_kn_sd, total_mf, total_mf_sd)
control_group <- c(c_rows, c_age, c_age_sd, c_ch, c_ch_sd, c_cd, c_emp, c_we, c_wo, c_kn,c_kn_sd, c_mf, c_mf_sd)
treatment_group <- c(t_rows, t_age, t_age_sd, t_ch, t_ch_sd, t_cd, t_emp, t_we, t_wo, t_kn, t_kn_sd, t_mf, t_mf_sd)
```

```{r}
#| message: false
#| echo: false
#| label: tbl-summary_table
#| tbl-cap: Summary Statistics (Main Experiment)
table1 <- cbind(total_group, control_group, treatment_group)
row.names(table1)= c("Observations","Age","","Number of Children","","College Degree (%)","Employed (%)","Wife Employed (%)", "Wife Working Outside the Home (% retrospective follow-up)", "Other Participants Known (%)", "","Other Participants with Mutual Friends (%)","")

table1 |> kbl(booktabs = T, col.names = c("All","Control","Treatment"), align=rep('c', 4)) |> 
  row_spec(1, hline_after = TRUE) |> kable_styling()
```
```{r}
#| message: false
#| echo: false
outside_value <- na.omit(online_survey_clean$c_outside_guess_frac)
group <- rep("Control", length(outside_value))
c_outside <- cbind(outside_value, group)
c_outside <- data.frame(c_outside)

outside_value <- na.omit(online_survey_clean$t_outside_guess_frac)
group <- rep("Treatment", length(outside_value))
t_outside <- cbind(outside_value, group)
t_outside <- data.frame(t_outside)
data_frame <- rbind(c_outside, t_outside)

c_mean <- mean(online_survey_clean$c_outside_mean)/100
t_mean <- mean(online_survey_clean$t_outside_mean)/100

data_frame <- data.frame(data_frame)
data_frame$group <- as.factor(data_frame$group)
data_frame$outside_value <- as.numeric(data_frame$outside_value)
```

```{r}
#| message: false
#| echo: false
#| label: fig-national_survey_misperception
#| fig-cap: Misperceptions about Others’ Beliefs (National Survey)
data_frame |>
  ggplot(aes(x = outside_value)) +
  theme_minimal() +
  stat_ecdf(aes(color = group, linetype = group), linewidth = 0.5) +
  scale_y_continuous(name = "Cumulative Probability", breaks = c(0,.2,.4,.6,.8,1), limits = c(0,1)) +
  scale_x_continuous(name = "Share of other agreeing", breaks = c(0,.2,.4,.6,.8,1), limits = c(0,1)) +
  theme(legend.position = "bottom", legend.title = element_blank(),
        legend.direction = "vertical",
        aspect.ratio = 0.5,
        legend.box.background = element_rect(color = "black", linewidth = 0.5)) +
  scale_linetype_discrete(labels = c("Control (perceptions about others' answers)", "Treatment (Perception about others' beliefs)")) +
  scale_colour_manual(values = c("black","tomato4"), labels = c("Control (perceptions about others' answers)", "Treatment (Perception about others' beliefs)")) +
  geom_vline(aes(xintercept = c_mean), col = "black")+
  geom_vline(aes(xintercept = t_mean), col="tomato4", linetype ="longdash") +
  annotate(geom = "text",
           label = c("True proportion\n(treatment)","True proportion\n(control)"),
           x = c(0.8, 1),
           y = 0.15,
           vjust = -1,
           hjust = 1,
           size = 2,
           col = c("black","black"))
```

### 2024-02-11 outputs/replication/replication.qmd
change the names of datasets

@@
 # Read the dataset
-main_clean <- read_dta(here("inputs/data/01_main_exp_clean.dta"))
-follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean.dta"))
-online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean.dta"))
+main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
+follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
+online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
 ```

### 2024-02-11 scripts/table_and_figure6.R
table

@@ -1,69 +1,198 @@
+
+
+# Install packages we need
+install.packages('haven')
+install.packages('dplyr')
+install.packages('ggplot2')
+install.packages('readr')
+install.packages('here')
+install.packages('janitor')
+install.packages('knitr')
+
+
 library(haven)
 library(dplyr)
-
-# Define the directory paths
-datadir <- "/cloud/project/inputs/data/"
-raw_data_path <- file.path(datadir, "raw_data/01_main_exp_raw2.dta")
-
-# Load the main experiment dataset
-df_main_exp <- read_dta(raw_data_path)
-
-# Adjust 'session' based on specific 'digits' values
-df_main_exp <- df_main_exp %>%
-  mutate(dup_index = row_number() + 1000) %>%
-  mutate(session = case_when(
-    session == 1 & digits == 136 ~ dup_index,
-    session == 5 & digits == 430 ~ dup_index,
-    session == 6 & digits == 651 ~ dup_index,
-    session == 6 & digits == 922 ~ dup_index,
-    session == 7 & digits == 646 ~ dup_index,
-    session == 9 & digits == 16 ~ dup_index,
-    session == 9 & digits == 449 ~ dup_index,
-    session == 12 & digits == 282 ~ dup_index,
-    session == 13 & digits == 880 ~ dup_index,
-    session == 15 & digits == 84 ~ dup_index,
-    session == 17 & digits == 341 ~ dup_index,
-    session == 17 & digits == 966 ~ dup_index,
-    TRUE ~ as.double(session)
-  ))
-
-# Load the follow-up dataset
-follow_up_path1 <- file.path(datadir, "raw_data/02_follow_up_raw1.dta")
-df_follow_up1 <- read_dta(follow_up_path1)
-
-# Merge the main experiment and follow-up datasets
-df_merged <- df_main_exp %>%
-  left_join(df_follow_up1, by = c("session", "digits"))
-
-# Flag matched rows based on 'work_outside_1_fl' being non-NA
-df_merged <- df_merged %>%
-  mutate(matched = if_else(!is.na(work_outside_1_fl), 1, 0))
-
-# Recode follow-up variables and perform further data manipulation
-df_clean <- df_merged %>%
[…]

### 2024-02-11 outputs/paper/paper.qmd
add one figure and one table to the paper

--- 2024-02-11 outputs/replication/replication.qmd
@@
 ---
-title: "Replication for figures and graphs"
-author: "Boxuan Yi, Ruoxian Wu"
+title: "My title"
+subtitle: "My subtitle if needed"
+author: 
+  - Boxuan Yi
+  - Ruoxian Wu
+thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia.
+Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1461/"
+date: "February 10, 2024"
+date-format: long
+abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 format: pdf
+toc: true
+number-sections: true
+bibliography: references.bib
 ---
@@
 
+# Introduction
+
+You can and should cross-reference sections and sub-sections.
+
+The remainder of this paper is structured as follows.
+
+# Data
+
+## Source
+
+## Methodology
+
+# Results
+## Figure 1 (Originally figure 2)
+
+## Table 1 (Originally table 1)
 ```{r}
@@
 # Read the dataset
-main_clean <- read_dta(here("inputs/data/01_main_exp_clean.dta"))
-follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean.dta"))
-online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean.dta"))
-```
-
-```{r}
-#| include: false
-# Test
-main_clean$condition2 |> unique()
+main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
+follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
+online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
 ```
@@
 ```
+## Figure 2 (Originally figure 4)
+
+## Figure 3 (Originally figure 6)
 ```{r}
@@
 ```
+
+# Discussion
+
+## First discussion point
+
+## Second discussion point
+
+## Third discussion point
+
+## Bias
+
+## Weaknesses and next steps
+
+\newpage
+
+\appendix
+
+# Appendix {-}
+
+# Additional data details
+
+\newpage
+
+# References

### 2024-02-11 outputs/paper/paper.qmd

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia"
 author: 
@@
 install.packages('knitr')
-install.packages("kableExtra")
+install.packages('kableExtra')
 ```

### 2024-02-11 r_code/Figure4.R
figure

@@ -44,27 +44,33 @@ df_stats <- df_filtered %>%
   select(-n) # Optionally dropping 'n' after calculations
 
 
+# p values
+p_value_applied <- t.test(applied_out_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+p_value_interviewed <- t.test(interviewed_out_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+p_value_employed_now <- t.test(employed_now_out_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+p_value_driving <- t.test(driving_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
 
 
-# Conduct a t-test for 'min_wage_fl_per' by 'condition'
-# Ensure 'min_wage_fl_per' and 'condition' exist in 'df_filtered'
-ttest_result <- t.test(min_wage_fl_per ~ factor(condition), data = df_filtered)
-pvalue <- ttest_result$p.value
-
-# Plot for Applied Rate
 applied_rate_4a <- ggplot(df_stats, aes(x = factor(condition), y = applied_rate)) +
   geom_bar(stat = "identity", fill = "skyblue", color = "black", width = 0.7) +
   geom_errorbar(aes(ymin = applied_rate_lo, ymax = applied_rate_hi), width = 0.2, color = "black") +
+  geom_text(aes(label = sprintf("%.2f%%", applied_rate), y = applied_rate + 1), position = position_dodge(width = 0.7), vjust = 0) +
+  annotate("text", x = 1, y = max(df_stats$applied_rate_hi) + 3, label = paste("p-value =", round(p_value_applied, 3)), size = 4) +
   labs(x = "", y = "% Applied", title = "Long-Term Labor Supply Outcomes") +
   theme_minimal() +
   scale_x_discrete(labels = c("Control", "Treatment"))
 
+
+
 ggsave("/cloud/project/outputs/figures/applied_rate_4a.png", plot = applied_rate_4a, width = 8, height = 6)
 
 # Interviewed Rate
+
 interviewed_rate_4b <- ggplot(df_stats, aes(x = factor(condition), y = interviewed_rate)) +
   geom_bar(stat = "identity", fill = "yellow", color = "black", width = 0.7) +
[…]

### 2024-02-11 r_code/table_and_figure6.R
table code

@@ -21,9 +21,9 @@ library(kableExtra)
 
 
 # Read the dataset
-main_clean <- read_dta(here("inputs/data/01_main_exp_clean.dta"))
-follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean.dta"))
-online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean.dta"))
+main_clean <- read_dta(here("inputs/data/clean_data/01_main_exp_clean.dta"))
+follow_up_clean <- read_dta(here("inputs/data/clean_data/02_follow_up_clean.dta"))
+online_survey_clean <- read_dta(here("inputs/data/clean_data/original03_1st_online_svy_clean.dta"))
 
 
 # Test
@@ -149,7 +149,7 @@ row.names(table1)= c("Observations","Age","","Number of Children","","College De
 table1 |> kbl(booktabs = T, col.names = c("All","Control","Treatment"), align=rep('c', 4)) |> 
   row_spec(1, hline_after = TRUE) |> kable_styling()
 
-
+write.csv(table1, file = "/cloud/project/outputs/table/table1.csv", row.names = FALSE)
 
 
 
@@ -174,7 +174,8 @@ data_frame$outside_value <- as.numeric(data_frame$outside_value)
 
 
 
-data_frame |>
+figure6 <-
+  data_frame |>
   ggplot(aes(x = outside_value)) +
   theme_minimal() +
   stat_ecdf(aes(color = group, linetype = group), linewidth = 0.5) +
@@ -196,3 +197,6 @@ data_frame |>
            hjust = 1,
            size = 2,
            col = c("black","black"))
+
+ggsave("/cloud/project/outputs/figures/figure6.png", plot = figure6)
+

### 2024-02-11 outputs/paper/paper.qmd
create one more figure to the paper

@@
 # Results
-## Figure 1 (Originally figure 2)
-
-## Table 1 (Originally table 1)
 ```{r}
@@
 ```
+
+## Figure 1 (Originally figure 2)
+
+## Figure 2 (Originally figure 3)
+```{r}
+#| message: false
+#| echo: false
+p_value_figure3 <- chisq.test(table(main_clean$condition2, main_clean$signed_up_number))
+
+percentage_data_figure3 <- main_clean |>
+  mutate(condition2 = ifelse(condition2 == 0, 'Control', 'Treatment')) |>
+  group_by(condition2) |>
+  summarise(percentage = mean(signed_up_number == 1) * 100)
+```
+
+```{r}
+#| message: false
+#| echo: false
+#| label: fig-job_sign_up
+#| fig-cap: Job Matching Service Sign Up (Main Experiment)
+plot_figure3 <- ggplot(percentage_data_figure3, aes(x = condition2, y = percentage)) +
+  geom_bar(stat = "identity", fill = "grey", color = "black", alpha = 0.9) +
+  labs(x = "",
+       y = "Percent sign up") +
+  geom_text(aes(label = paste0(round(percentage, 2), "%")),
+            position = position_dodge(width = 0.9),
+            vjust = -0.5) +
+  annotate("text", x = 1.5, y = 37, label = sprintf("p-value = %.4f", p_value_figure3$p.value)) +
+  theme_minimal() + 
+  ylim(0, 40)
+
+plot_figure3
+```
+
+## Table 1 (Originally table 1)
 

### 2024-02-12 r_code/Figure2.R
fig 2

@@ -21,18 +21,27 @@ df[[paste0(q, "_wedge_share")]] <- (df[[paste0(q, "_wedge")]] / 30) * 100
 
 # Plotting a histogram of the wedge share
 f2 <- ggplot(df, aes(x = .data[[paste0(q, "_wedge_share")]])) +
-  geom_histogram(binwidth = 10.5, fill = "#d3d3d3", color = "black") +
-  scale_x_continuous("Wedge (guess % - objective %)", breaks = seq(-100, 100, by = 20)) +
-  scale_y_continuous("Density", expand = c(0, 0)) +
-  geom_vline(xintercept = 0, linetype = "dashed", color = "red") +
-  theme_minimal() +
+  geom_histogram(binwidth = 10.5, fill = "lightgrey", color = "black") + # Adjust fill for contrast
+  scale_x_continuous("Wedge (guess % - objective %)", 
+                     breaks = seq(-100, 100, by = 10), 
+                     limits = c(-100, 100), # Explicitly set x-axis limits
+                     expand = c(0, 0.5)) +
+  scale_y_continuous("Density", expand = c(0.5, 0)) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "#FF4136", size = 0.5) + # Less prominent zero line
+  labs(title = "Distribution of Wedge (Guess % - Objective %)", # Add a title
+       caption = "Red dashed line represents the zero point") + # Add a caption
+  theme_minimal(base_size = 12) + # Use theme_minimal with a base font size
   theme(
     plot.background = element_blank(),
-    axis.text = element_text(size = 12),
-    axis.title = element_text(size = 14),
-    panel.grid.major = element_line(color = "#e5e5e5"),
-    panel.grid.minor = element_blank()
+    panel.background = element_rect(fill = "white", colour = "black"), # White background with border
+    axis.text = element_text(size = 12, color = "black"), # Ensure text is black for readability
+    axis.title = element_text(size = 14, color = "black"),
+    panel.grid.major = element_line(color = "lightgrey", size = 0.2), # Subtle gridlines
+    panel.grid.minor = element_blank(),
+    plot.title = element_text(hjust = 0.5), # Center the title
+    plot.caption = element_text(hjust = 0.5) # Center the caption
   )
+f2
 
 
 # Save the cleaned data

### 2024-02-12 outputs/paper/paper.qmd
paper

--- 2024-02-11 outputs/paper/paper.qmd
@@
 # Results
-## Figure 1 (Originally figure 2)
+
+The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
+The negative wedge indicates that the participant underestimated the support for WWOH.
+Conversely, a positive wedge suggests that the participant overestimated the support for WWOH.
+We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
+@fig-1 specifically maps the distribution of these "wedges" – the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
+It was found that more than half of participants underestimated the support for WWOH.
+There is a clear gap between perceived and actual social norms regarding women's work outside the home.
+The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.
+
+```{r}
+#| include: false
+# Define the path
+datadir <- "/cloud/project/inputs/data/"
+data_path <- file.path(datadir, "clean_data/01_main_exp_clean.dta")
+
+# Load the dataset
+df <- read_dta(data_path)
+
+# Define the variable prefix
+q <- "outside"
+
+# Create new variables
+df[[paste0(q, "_guess_share")]] <- df[[paste0(q, "_guess")]] / 30
+df[[paste0(q, "_others_truth")]] <- ifelse(df$stag == 1, df[[paste0(q, "_objective")]] / 30, NA)
+q_self_mean <- mean(df[[paste0(q, "_self")]], na.rm = TRUE)
+df[[paste0(q, "_wedge_share")]] <- (df[[paste0(q, "_wedge")]] / 30) * 100
+
+```
+
+```{r}
+#| label: fig-1
+#| fig-cap: Histogram of Perceptual Gaps in Beliefs About Women Working Outside the Home
+#| echo: false
+#| warning: false
+#| message: false
+
+# Plotting a histogram of the wedge share
+f2 <- ggplot(df, aes(x = .data[[paste0(q, "_wedge_share")]])) +
+  geom_histogram(binwidth = 10.5, fill = "lightgrey", color = "black") + 
+  scale_x_continuous("Wedge (guess % - objective %)", 
+                     breaks = seq(-100, 100, by = 20), 
+                     limits = c(-100, 100), 
+                     expand = c(0.1, 0.5)) +
+  scale_y_continuous("Density", expand = c(0.5, 0)) +
+  geom_vline(xintercept = 0, linetype = "dashed", color = "#FF4136", size = 0.5) + # Less prominent zero line
+  labs(title = "Distribution of Wedge (Guess % - Objective %)", # Add a title
+       caption = "Red dashed line represents the zero point") + # Add a caption
+  theme_minimal(base_size = 12) + 
+  theme(
+    plot.background = element_blank(),
+    panel.background = element_rect(fill = "white", colour = "black"), 
+    axis.text = element_text(size = 12, color = "black"), 
+    axis.title = element_text(size = 14, color = "black"),
+    panel.grid.major = element_line(color = "lightgrey", size = 0.2), 
+    panel.grid.minor = element_blank(),
+    plot.title = element_text(hjust = 0.5), 
+    plot.caption = element_text(hjust = 0.5) 
+  )
+f2
+```
 
@@
 ## Figure 2 (Originally figure 4)
+```{r}
+#| include: false
+# Define path 
+datadir <- "/cloud/project/inputs/data/"
+data_path <- file.path(datadir, "clean_data/02_follow_up_clean.dta")
+
+# Load the dataset
+df <- read_dta(data_path)
+
+# Keep matched responses and rename variable if necessary
+df_filtered <- df %>%
+  filter(matched == 1)
+
+# Calculate rates and their confidence intervals
+df_stats <- df_filtered %>%
+  mutate(condition = if_else(is.na(condition), 0, condition)) %>%
+  group_by(condition) %>%
+  summarise(
+    n = n(),
+    applied_rate = mean(applied_out_fl, na.rm = TRUE) * 100,
+    interviewed_rate = mean(interviewed_out_fl, na.rm = TRUE) * 100,
+    employed_now_rate = mean(employed_now_out_fl, na.rm = TRUE) * 100,
+    driving_rate = mean(driving_fl, na.rm = TRUE) * 100 
+  ) %>%
+  mutate(
+    applied_se = sqrt((applied_rate / 100) * (1 - (applied_rate / 100)) / n) * 100,
+    applied_rate_lo = applied_rate - 1.96 * applied_se,
+    applied_rate_hi = applied_rate + 1.96 * applied_se,
+    interviewed_se = sqrt((interviewed_rate / 100) * (1 - (interviewed_rate / 100)) / n) * 100,
+    interviewed_rate_lo = interviewed_rate - 1.96 * interviewed_se,
+    interviewed_rate_hi = interviewed_rate + 1.96 * interviewed_se,
+    employed_now_se = sqrt((employed_now_rate / 100) * (1 - (employed_now_rate / 100)) / n) * 100,
+    employed_now_rate_lo = employed_now_rate - 1.96 * employed_now_se,
+    employed_now_rate_hi = employed_now_rate + 1.96 * employed_now_se,
+    driving_se = sqrt((driving_rate / 100) * (1 - (driving_rate / 100)) / n) * 100, 
+    driving_rate_lo = driving_rate - 1.96 * driving_se,  
+    driving_rate_hi = driving_rate + 1.96 * driving_se   
+  ) %>%
+  select(-n)
+
+# p values
+p_value_applied <- t.test(applied_out_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+p_value_interviewed <- t.test(interviewed_out_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+p_value_employed_now <- t.test(employed_now_out_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+p_value_driving <- t.test(driving_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
+
+```
+By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives.
+The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899.
+The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment.
+The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038.
+These results reinforcing the treatment's positive impact on sign-up rates @tbl-summary_table.
+
+## Figure 2 original fig 3
+Fig-2 illustrates the difference in job matching service sign-up rates between the control and treatment groups.
+The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment.
+The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.017, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.
+
+```{r}
+#| label: fig-3
+#| fig-cap: Histogram of Perceptual Gaps in Beliefs About Women Working Outside the Home
+#| echo: false
+#| warning: false
+#| message: false
+#| layout-ncol: 2
+#| fig-subcap: ["Applied Rate","Interviewed Rate", "Employed Now Rate", "Driving Rate"]
+
+# Applied Rate
+applied_rate_4a <- ggplot(df_stats, aes(x = factor(condition), y = applied_rate)) +
+  geom_bar(stat = "identity", fill = "skyblue", color = "black", width = 0.7) +
+  geom_errorbar(aes(ymin = applied_rate_lo, ymax = applied_rate_hi), width = 0.2, color = "black") +
+  geom_text(aes(label = sprintf("%.2f%%", applied_rate), y = applied_rate + 1), position = position_dodge(width = 0.7), vjust = 0) +
+  annotate("text", x = 1, y = max(df_stats$applied_rate_hi) + 3, label = paste("p-value =", round(p_value_applied, 3)), size = 4) +
+  labs(x = "", y = "% Applied", title = "Long-Term Labor Supply Outcomes") +
+  theme_minimal() +
+  scale_x_discrete(labels = c("Control", "Treatment"))
+
+applied_rate_4a
+
+# Interviewed Rate
+
+interviewed_rate_4b <- ggplot(df_stats, aes(x = factor(condition), y = interviewed_rate)) +
+  geom_bar(stat = "identity", fill = "yellow", color = "black", width = 0.7) +
+  geom_errorbar(aes(ymin = interviewed_rate_lo, ymax = interviewed_rate_hi), width = 0.2, color = "black") +
+  geom_text(aes(label = sprintf("%.2f%%", interviewed_rate), y = interviewed_rate_hi + 2), vjust = 0) +
+  annotate("text", x = 1.5, y = max(df_stats$interviewed_rate_hi) + 5, label = paste("p-value =", round(p_value_interviewed, 3)), size = 4) +
+  labs(y = "% Interviewed", x = "") +
+  theme_minimal() +
+  scale_x_discrete(labels = c("Control", "Treatment"))
+
+interviewed_rate_4b
+
+# Employed Now Rate
+
+employed_rate_4c <- ggplot(df_stats, aes(x = factor(condition), y = employed_now_rate)) +
+  geom_bar(stat = "identity", fill = "lightgreen", color = "black", width = 0.7) +
+  geom_errorbar(aes(ymin = employed_now_rate_lo, ymax = employed_now_rate_hi), width = 0.2, color = "black") +
+  geom_text(aes(label = sprintf("%.2f%%", employed_now_rate), y = employed_now_rate_hi + 2), vjust = 0) +
+  annotate("text", x = 1.5, y = max(df_stats$employed_now_rate_hi) + 5, label = paste("p-value =", round(p_value_employed_now, 3)), size = 4) +
+  labs(y = "% Employed Now", x = "") +
+  theme_minimal() +
+  scale_x_discrete(labels = c("Control", "Treatment"))
+
+employed_rate_4c
+
+# Driving Rate
+driving_rate_4d <- ggplot(df_stats, aes(x = factor(condition), y = driving_rate)) +
+  geom_bar(stat = "identity", fill = "lightpink", color = "black", width = 0.7) +
+  geom_errorbar(aes(ymin = driving_rate_lo, ymax = driving_rate_hi), width = 0.2, color = "black") +
+  geom_text(aes(label = sprintf("%.2f%%", driving_rate), y = driving_rate_hi + 2), vjust = 0) +
+  annotate("text", x = 1.5, y = max(df_stats$driving_rate_hi) + 5, label = paste("p-value =", round(p_value_driving, 3)), size = 4) +
+  labs(y = "% Driving", x = "Condition") +
+  theme_minimal() +
+  scale_x_discrete(labels = c("Control", "Treatment"))
+
+driving_rate_4d
+```
 

### 2024-02-12 outputs/paper/paper—copy.qmd

--- 2024-02-12 outputs/paper/paper.qmd
@@
 We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
-@fig-1 specifically maps the distribution of these "wedges" – the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
+@fig-1 specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
 It was found that more than half of participants underestimated the support for WWOH.
@@
 
-## Table 1 (Originally table 1)
+### Table 1 (Originally table 1)
+
 ```{r}
@@
 ```
+
+## Figure 1 (Originally figure 2)
+
+## Figure 2 (Originally figure 3)
+
+```{r}
+#| message: false
+#| echo: false
+p_value_figure3 <- chisq.test(table(main_clean$condition2, main_clean$signed_up_number))
+
+percentage_data_figure3 <- main_clean |>
+  mutate(condition2 = ifelse(condition2 == 0, 'Control', 'Treatment')) |>
+  group_by(condition2) |>
+  summarise(percentage = mean(signed_up_number == 1) * 100)
+```
+
+```{r}
+#| message: false
+#| echo: false
+#| label: fig-job_sign_up
+#| fig-cap: Job Matching Service Sign Up (Main Experiment)
+plot_figure3 <- ggplot(percentage_data_figure3, aes(x = condition2, y = percentage)) +
+  geom_bar(stat = "identity", fill = "grey", color = "black", alpha = 0.9) +
+  labs(x = "",
+       y = "Percent sign up") +
+  geom_text(aes(label = paste0(round(percentage, 2), "%")),
+            position = position_dodge(width = 0.9),
+            vjust = -0.5) +
+  annotate("text", x = 1.5, y = 37, label = sprintf("p-value = %.4f", p_value_figure3$p.value)) +
+  theme_minimal() + 
+  ylim(0, 40)
+
+plot_figure3
+```
+
+## Table 1 (Originally table 1)
 
@@
 ```
+
 ## Figure 2 (Originally figure 4)
+
 ```{r}
@@
 ```
+
 By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives.
@@
 ## Figure 2 original fig 3
+
 Fig-2 illustrates the difference in job matching service sign-up rates between the control and treatment groups.
@@
 ## Figure 3 (Originally figure 6)
+
 ```{r}
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 

### 2024-02-12 outputs/paper/paper.qmd
papers

@@
 # Results
+```{r}
+#| message: false
+#| echo: false
+# Read the dataset
+main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
+follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
+online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
+```
 
-The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
-The negative wedge indicates that the participant underestimated the support for WWOH.
-Conversely, a positive wedge suggests that the participant overestimated the support for WWOH.
-We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
-@fig-1 specifically maps the distribution of these "wedges" – the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
-It was found that more than half of participants underestimated the support for WWOH.
-There is a clear gap between perceived and actual social norms regarding women's work outside the home.
-The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.
+## Figure 1 (Originally figure 2)
 
@@
 
+The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
+The negative wedge indicates that the participant underestimated the support for WWOH.
+Conversely, a positive wedge suggests that the participant overestimated the support for WWOH.
+We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
+@fig-1 specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
+It was found that more than half of participants underestimated the support for WWOH.
+There is a clear gap between perceived and actual social norms regarding women's work outside the home.
+The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.
+
 ## Table 1 (Originally table 1)
-```{r}
-#| message: false
-#| echo: false
-# Read the dataset
-main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
-follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
-online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
-```
+By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives.
+The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899.
+The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment.
+The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038.
+These results reinforcing the treatment's positive impact on sign-up rates (@tbl-summary_table).
 
@@
 ```
-## Figure 2 (Originally figure 4)
+
+## Figure 2 (Originally figure 3)
+```{r}
+#| message: false
+#| echo: false
+p_value_figure3 <- chisq.test(table(main_clean$condition2, main_clean$signed_up_number))
+
+percentage_data_figure3 <- main_clean |>
+  mutate(condition2 = ifelse(condition2 == 0, 'Control', 'Treatment')) |>
+  group_by(condition2) |>
+  summarise(percentage = mean(signed_up_number == 1) * 100)
+```
+
+```{r}
+#| message: false
+#| echo: false
+#| label: fig-job_sign_up
+#| fig-cap: Job Matching Service Sign Up (Main Experiment)
+plot_figure3 <- ggplot(percentage_data_figure3, aes(x = condition2, y = percentage)) +
+  geom_bar(stat = "identity", fill = "grey", color = "black", alpha = 0.9) +
+  labs(x = "",
+       y = "Percent sign up") +
+  geom_text(aes(label = paste0(round(percentage, 2), "%")),
+            position = position_dodge(width = 0.9),
+            vjust = -0.5) +
+  annotate("text", x = 1.5, y = 37, label = sprintf("p-value = %.4f", p_value_figure3$p.value)) +
+  theme_minimal() + 
+  ylim(0, 40)
+
+plot_figure3
+```
+
+@fig-job_sign_up illustrates the difference in job matching service sign-up rates between the control and treatment groups.
+The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment.
+The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.017, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.
+
+The combination of @tbl-summary_table and @fig-job_sign_up demonstrates the efficacy of the information treatment in altering the participants' behavior towards women's labor market participation, revealing not only a statistical significance but also practical importance in the context of social norms and labor supply outcomes in Saudi Arabia.
+
+## Figure 3 (Originally figure 4)
+The the longer-term outcomes of the treatment are shown in @fig-3 with error bars indicating the 95% confidence intervals for these proportions.
+
+The job matching service sign-up rates is presented in Figure 4a.
+In the control group, 6.04% of participants chose to sign their wives up for the job service instead of taking a gift card payment while 16.74% participants in the treatment group chose the job service (p-value = 0.001).
+The increased sign-up rate in the treatment group more young men accepted the idea of WWOH after the correction of misperceptions.
+
+The informational intervention has impact on participants' wives were interviewed for a job outside the home.
+After the intervention, there was a statistically significant increase in interviews, with the percentage of wives who interviewed for a job outside the home rising from 1.1% to 5.95%.
+This more than fivefold increase (p-value = 0.013) suggests that the treatment had a notable effect on the interview rates for jobs outside the home (Figure 4b).
+
+Similarly, the informational intervention effects on the employment rate of participants' wives in jobs outside the home.
+The employment rate post-intervention increased from 7.69% to 9.73%.
+Although this represents an increase, it is not statistically significant (p-value = 0.456), implying that while the intervention might have had an encouraging effect on job-seeking behavior, it did not translate into a significant difference in actual employment within the study period (Figure 4c).
+
+Besides, Figure 4d indicates that the change in husbands' willingness to sign their wives up for driving lessons as a result of the informational intervention.
+There is a significant increase from 68.13% to 78.38% in the proportion of husbands who reported they would sign their wives up for driving lessons (p-value = 0.03).
+This result indicates that the informational intervention not only had an impact on labor supply outcomes but also potentially affected broader social norms and attitudes toward women's rights and autonomy in Saudi Arabia, as evidenced by the increased openness to women's mobility through driving.
+
+Overall, the treatment has a significant impact on both immediate and longer-term outcomes related to women's labor market participation and related behaviors (@fig-3).
+
 ```{r}
@@
 ```
-By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives.
-The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899.
-The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment.
-The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038.
-These results reinforcing the treatment's positive impact on sign-up rates @tbl-summary_table.
-
-## Figure 2 original fig 3
-Fig-2 illustrates the difference in job matching service sign-up rates between the control and treatment groups.
-The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment.
-The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.017, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.
 
@@
 
-## Figure 3 (Originally figure 6)
+\newpage
+## Figure 4 (Originally figure 6)
+@fig-national_survey_misperception is made to illustrate the result of the first national survey.
+There are two vertical lines that represent the actual proportion of respondents who agreed with the statement in Figure 6.
+One line is for the control group, which reflects their perceptions about others' answers, and the other line is for the treatment group, which reflects their perceptions about others' beliefs.
+The graph shows the support level of treatment group is mostly higher than control.
+This figure underscores a significant discrepancy between personal beliefs and perceived societal norms.
+The larger sample size of this national survey strengthens the evidence that men privately support women's employment outside the home more than they assume others do, suggesting widespread misperceptions about societal norms.
+
 ```{r}

### 2024-02-12 outputs/paper/paper.qmd
correct typo, include introduction

@@
 # Introduction
+Barriers to hiring women exert a significant influence on female labor and present a constraint to increasing economic opportunities for women [@Organizational].
+Saudi Arabia is a recognizable example of a country with a low rate of female labor force participation.
+In 2022, the female labor force participation rate, defined as the percentage of the female population aged 15+ that is employed, is only 27.8% in Saudi Arabia.
+This is notably lower than the global average of 47.3%, while the male labor force participation rate in Saudi Arabia is relatively high at 80% [@worldbankLaborForce].
 
-You can and should cross-reference sections and sub-sections.
+The prevailing societal norms in Saudi Arabia, characterized by a low rate of women working outside the home and the customary practice of husbands' guardianship with decision-making authority, contribute to the perception that Saudi men are unwilling to allow their wives to work [@MisperceivedSocialNorm].
+This perception is often considered the primary reason behind the low rates of female employment, especially female working outside the home (WWOH).
+The paper ‘Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia’ by Leonardo Bursztyn, Alessandra L.
+González, and David Yanagizawa-Drott delves into this social norm, as well as Saudi men’s perceptions of opinions regarding WWOH.
 
-The remainder of this paper is structured as follows.
+Drawing from survey responses and experiments results, they find that a large portion of young married men in Saudi Arabia privately support women working outside the home, and they greatly underestimate the proportion of support by other similar men [@MisperceivedSocialNorm].
+The study population is young married husbands in Saudi Arabia.
+We aim to replicate the estimand that focuses on the proportion of husbands signing up job matching for their wives and the subsequent employment of wives a few months after the experiment.
+Their findings suggest that men who are given the actual proportion of their peers supporting WWOH are more likely to support their wives’ labor supply, and their wives are more likely to apply for job, attend interviews, be employed and enrol in driving lessons.
+Correcting misperceived beliefs manifests positive impacts on females, and the lack of communication emerges as a primary factor contributing to these misperceptions.
+
+Our paper will follow a reproduction of Leonardo Bursztyn, Alessandra L.
+González, and David Yanagizawa-Drott’s findings.
+We seek to replicate two claims, (1) There is a wedge between the actual and perceived proportion of men supporting women working outside the home, and (2) Most Saudi men who privately support WWOH fail to understand that others do as well, and they are more likely to help their wives find jobs when they know the actual portion of men supporting WWOH.
+The experiments and surveys results we will try to replicate are (1) the actual portion of support of WWOH from young husbands, (2) the existence of misperception, and (3) the effects of correcting beliefs on wives in Saudi Arabia.
+Our reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr].
+
+In the next section, we will discuss data including data source, methodology and features.
+After that, we will create a reproduction of the selected results to verify their data and their findings based on the data.
+In the last section, we will discuss our findings, including ….
+We will also conclude potential bias and weaknesses, as well as a push for future research
 
@@
 
-## Methodology
+## Methodology and Features
+### Main experiment and Follow-up
+
+### Online survey
+
+### Women recruitment survey
 
@@
 ```
-
-## Figure 1 (Originally figure 2)
 
@@
 
-## Table 1 (Originally table 1)
 By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives.
@@
 
-## Figure 2 (Originally figure 3)
 ```{r}
@@
 The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment.
-The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.017, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.
+The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.0424, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.
 
@@
 
-## Figure 3 (Originally figure 4)
 The the longer-term outcomes of the treatment are shown in @fig-3 with error bars indicating the 95% confidence intervals for these proportions.
 
-The job matching service sign-up rates is presented in Figure 4a.
+The job matching service sign-up rates is presented in @fig-3 a.
 In the control group, 6.04% of participants chose to sign their wives up for the job service instead of taking a gift card payment while 16.74% participants in the treatment group chose the job service (p-value = 0.001).
@@
 
-The informational intervention has impact on participants' wives were interviewed for a job outside the home.
+In @fig-3 b, the informational intervention has impact on participants' wives were interviewed for a job outside the home.
 After the intervention, there was a statistically significant increase in interviews, with the percentage of wives who interviewed for a job outside the home rising from 1.1% to 5.95%.
-This more than fivefold increase (p-value = 0.013) suggests that the treatment had a notable effect on the interview rates for jobs outside the home (Figure 4b).
+This more than fivefold increase (p-value = 0.013) suggests that the treatment had a notable effect on the interview rates for jobs outside the home.
 
-Similarly, the informational intervention effects on the employment rate of participants' wives in jobs outside the home.
+Similarly, the informational intervention effects on the employment rate of participants' wives in jobs outside the home according to @fig-3 c.
 The employment rate post-intervention increased from 7.69% to 9.73%.
-Although this represents an increase, it is not statistically significant (p-value = 0.456), implying that while the intervention might have had an encouraging effect on job-seeking behavior, it did not translate into a significant difference in actual employment within the study period (Figure 4c).
+Although this represents an increase, it is not statistically significant (p-value = 0.456), implying that while the intervention might have had an encouraging effect on job-seeking behavior, it did not translate into a significant difference in actual employment within the study period.
 
-Besides, Figure 4d indicates that the change in husbands' willingness to sign their wives up for driving lessons as a result of the informational intervention.
+Besides, @fig-3 d indicates that the change in husbands' willingness to sign their wives up for driving lessons as a result of the informational intervention.
 There is a significant increase from 68.13% to 78.38% in the proportion of husbands who reported they would sign their wives up for driving lessons (p-value = 0.03).
@@
 \newpage
-## Figure 4 (Originally figure 6)
 @fig-national_survey_misperception is made to illustrate the result of the first national survey.
-There are two vertical lines that represent the actual proportion of respondents who agreed with the statement in Figure 6.
-One line is for the control group, which reflects their perceptions about others' answers, and the other line is for the treatment group, which reflects their perceptions about others' beliefs.
+There are two vertical lines that represent the actual proportion of respondents who agreed with the statement in @fig-national_survey_misperception, showing more than 80% of men underestimated the true proportion.
+The black line is for the control group, which reflects their perceptions about others' answers, and the red dashed line is for the treatment group, which reflects their perceptions about others' beliefs.
 The graph shows the support level of treatment group is mostly higher than control.
@@
 
-## Bias
+## Bias and Weaknesses
 
-## Weaknesses and next steps
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
+## Next steps
 

### 2024-02-12 r_code/table_and_figure6_and_figure3.R

@@ -1,15 +1,3 @@
-
-
-# Install packages we need
-install.packages('haven')
-install.packages('dplyr')
-install.packages('ggplot2')
-install.packages('readr')
-install.packages('here')
-install.packages('janitor')
-install.packages('knitr')
-
-
 library(haven)
 library(dplyr)
 library(ggplot2)
@@ -152,7 +140,27 @@ table1 |> kbl(booktabs = T, col.names = c("All","Control","Treatment"), align=re
 write.csv(table1, file = "/cloud/project/outputs/table/table1.csv", row.names = FALSE)
 
 
+# Figure 3
+p_value_figure3 <- chisq.test(table(main_clean$condition2, main_clean$signed_up_number))
+percentage_data_figure3 <- main_clean |>
+  mutate(condition2 = ifelse(condition2 == 0, 'Control', 'Treatment')) |>
+  group_by(condition2) |>
+  summarise(percentage = mean(signed_up_number == 1) * 100)
 
+plot_figure3 <- ggplot(percentage_data_figure3, aes(x = condition2, y = percentage)) +
+  geom_bar(stat = "identity", fill = "grey", color = "black", alpha = 0.9) +
+  labs(x = "",
+       y = "Percent sign up") +
+  geom_text(aes(label = paste0(round(percentage, 2), "%")),
+            position = position_dodge(width = 0.9),
+            vjust = -0.5) +
+  annotate("text", x = 1.5, y = 37, label = sprintf("p-value = %.4f", p_value_figure3$p.value)) +
+  theme_minimal() + 
+  ylim(0, 40)
+ggsave("/cloud/project/outputs/figures/figure3.png", plot = plot_figure3)
+
+
+# Figure 6
 outside_value <- na.omit(online_survey_clean$c_outside_guess_frac)
 group <- rep("Control", length(outside_value))
 c_outside <- cbind(outside_value, group)
@@ -170,8 +178,6 @@ t_mean <- mean(online_survey_clean$t_outside_mean)/100
 data_frame <- data.frame(data_frame)
 data_frame$group <- as.factor(data_frame$group)
 data_frame$outside_value <- as.numeric(data_frame$outside_value)
-
-
 
 
 figure6 <-

### 2024-02-12 scripts/01-test.R

@@ -1,3 +1,5 @@
 #### Preamble ####
 # Purpose: Testing datasets
 # Author: Boxuan Yi, Ruoxian Wu
+
+#

### 2024-02-12 scripts/03-01-clean_data.R

@@ -1,3 +1,7 @@
+#### Preamble ####
+# Purpose: Clean the raw dataset
+# Author: Boxuan Yi, Ruoxian Wu
+
 # Load necessary packages
 library(dplyr)
 library(haven)

### 2024-02-12 scripts/03-02-clean_following_up_data.R

@@ -1,3 +1,7 @@
+#### Preamble ####
+# Purpose: Clean the raw dataset
+# Author: Boxuan Yi, Ruoxian Wu
+
 library(haven)
 library(dplyr)
 

### 2024-02-12 scripts/03-clean.R

@@ -1,4 +1,0 @@
-#### Preamble ####
-# Purpose: Cleaning raw data collected from surveys prior to analysis.
-# Author: Boxuan Yi, Ruoxian Wu
-# Pre-requisites: Have raw datasets

### 2024-02-12 outputs/paper/paper.qmd
contains data, bias, and next steps in the paper

@@
 Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1461/"
-date: "February 10, 2024"
+date: "February 12, 2024"
 date-format: long
@@
 # Data
+## Source
+The paper used for replication is from American Economic Association, American Economic Review.
+The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials.
 
-## Source
+Our reproduction seeks to address two findings written in the original paper, using results they collected from the main experiment, its follow-up and online survey.
 
@@
 ### Main experiment and Follow-up
+The original study recruited 500 married Saudi males aged 18 to 35 from Riyadh as participants.
+Initial contacts were established using a recruiter database, with further recruitment using a combination of snowball sampling and random street intercept [@MisperceivedSocialNorm].
+
+Participants were organized into 17 sessions, each comprising 30 individuals.
+The survey, administered through Qualtrics, encompassed questions about demographic information, opinions, agreement with statements, and estimations regarding the agreement of other  29 participants with each statement.
+Particularly, there were two statements about female labor participation.
+Following this, half of the participants were assigned to a treatment group randomly.
+Those in the treatment group were provided with information on the proportion of respondents who agreed or disagreed with each statement, while participants in the control group received no information.
+Respondents were then asked to make an incentivized choice between a five-dollar Amazon gift card and the opportunity to sign up their wives for a job matching platform [@MisperceivedSocialNorm].
+Follow-up calls were conducted 3-5 months after the main experiment.
+These calls collected information about whether the wife was employed during the main experiment, whether the wife was currently employed, and if she was currently employed, whether the job was outside the home [@MisperceivedSocialNorm].
+
+The main experiment dataset contains 500 observations and 36 variables.
+Variables include age, level of education, number of children, whether this man and his wife are employed now, number of people known in the group and other variables related to WWOH statements.
+The follow-up dataset contains similar demographic data and information about wives’ employment, interviews and driving lessons.
+There are 33 variables in the follow-up dataset.
+Details and explanations using visualization will be further discusses in the next section.
 
 ### Online survey
+The online survey included approximately 1500 married Saudi men aged 18 to 35, randomly assigned to either a treatment or control group.
+In the control group, participants were presented with statements that were contentious but not stigmatized.
+In the treatment group, participants received an identical list of items with an additional, potentially stigmatized item for which the experimenters would like to elicit beliefs.
+All participants were then asked to indicate the number of statements they agree with, and the respondents from the control group were asked if they agreed with a WWOH statement individually [@MisperceivedSocialNorm].
+Finally, the experimenters asked participants in the control condition to estimate the percentage of other participants who reported agreeing with the same statement, and asked participants from the treatment group to estimate the percentage of other participants who would privately agree with the WWOH statement [@MisperceivedSocialNorm].
 
-### Women recruitment survey
+The dataset resulting from online survey comprises 1460 observations and 21 variables.
+These variables include condition, age, employed_now, employed_wife, employed_out_wife, children, and the responses to the survey questions for both groups as indicated above, along with participants’ confidence levels in some of the answers.
+Details and explanations using visualization will be further discusses in the next section.
 
@@
 ## Bias and Weaknesses
+The authors, Leonardo Bursztyn, Alessandra L.
+González, and David Yanagizawa-Drott, implemented many modifications to the questions and weights in an attempt to minimize bias in the survey.
+However, it is acknowledged that bias is an inherent challenge when conducting experiments.
+The main experiment survey has a participant pool of 500 married men from Riyadh.
+Since Riyadh is the capital and the largest city in Saudi Arabia, the sample size might be relatively small and potentially biased.
+The reward offered, typically a five-dollar or twenty-dollar gift card, could be another factor contributing to potential biases considering the GDP in Saudi Arabia.
+The paper focuses on married men aged 18 to 35 with some level of education.
+It is noted that, for the majority of individuals, the expected age range for completing college or university education is between 20 and 24.
+Therefore, setting the age range from 18 to 35 might be a weakness in the experiment.
+
+There is a potential correlation between individuals who did not participate in the follow-up and those who do not support Women Working Outside the Home, also introducing the possibility of bias.
 
 ## Next steps
+Although there is a customary practice of husbands' guardianship with decision-making authority in Saudi Arabia, gaining insights into the opinions of Saudi women regarding employment and working outside the home is essential for future study.
+The authors mentioned that ‘expanding the scale and observing how information spreads in networks, and how it affects a large set of outcomes is an important topic for future work’ [@MisperceivedSocialNorm].
+Considering the potential biases and the experiment result stating correcting misperceived beliefs increase husbands’ support in WWOH, future research could greatly benefit from the extension of scale to enhance generalizability and actual effects on female employment in Saudi society.
+
+Figure 9 in the original paper reveals that males who often engage in discussions about the WWOH exhibit perceived support only four percent smaller than the actual proportion.
+For those who rarely or very rarely discuss about the WWOH, their perceived support for WWOH is around forty percent smaller than the actual proportion.
+If the lack of communication facilitates misperceptions, one would expect a correlation between the frequency of communication and perceptions [@MisperceivedSocialNorm].
+Consequently, future studies could delve into strategies in preventing misperceived opinions from influencing social norms, and explore decision-making in the presence of collective misperceptions.
 

### 2024-02-12 outputs/paper/paper.qmd
modify references and discussion part

@@
 # Introduction
-Barriers to hiring women exert a significant influence on female labor and present a constraint to increasing economic opportunities for women [@Organizational].
+Barriers to the employment of women exert a significant influence on female labor, presenting a constraint to increasing economic opportunities for women [@sciencedirectOrganizationalEconomic].
 Saudi Arabia is a recognizable example of a country with a low rate of female labor force participation.
-In 2022, the female labor force participation rate, defined as the percentage of the female population aged 15+ that is employed, is only 27.8% in Saudi Arabia.
-This is notably lower than the global average of 47.3%, while the male labor force participation rate in Saudi Arabia is relatively high at 80% [@worldbankLaborForce].
+In 2022, the female labor force participation rate, defined as the percentage of the female population aged 15 and above that is employed, is only 27.8% in Saudi Arabia.
+This is notably lower than the global average of 47.3%, while the male labor force participation rate in Saudi Arabia remains high at 80% [@worldbankLaborForce].
 
-The prevailing societal norms in Saudi Arabia, characterized by a low rate of women working outside the home and the customary practice of husbands' guardianship with decision-making authority, contribute to the perception that Saudi men are unwilling to allow their wives to work [@MisperceivedSocialNorm].
-This perception is often considered the primary reason behind the low rates of female employment, especially female working outside the home (WWOH).
+The prevailing societal norms in Saudi Arabia, characterized by a low rate of women working outside the home and the customary practice of husbands' guardianship with decision-making authority, contribute to the perception that Saudi men are unwilling to permit their wives to work [@MisperceivedSocialNorm].
 The paper ‘Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia’ by Leonardo Bursztyn, Alessandra L.
-González, and David Yanagizawa-Drott delves into this social norm, as well as Saudi men’s perceptions of opinions regarding WWOH.
+González, and David Yanagizawa-Drott delves into this social norm, exploring Saudi men’s perceptions of opinions regarding WWOH.
 
-Drawing from survey responses and experiments results, they find that a large portion of young married men in Saudi Arabia privately support women working outside the home, and they greatly underestimate the proportion of support by other similar men [@MisperceivedSocialNorm].
-The study population is young married husbands in Saudi Arabia.
-We aim to replicate the estimand that focuses on the proportion of husbands signing up job matching for their wives and the subsequent employment of wives a few months after the experiment.
+Based on survey responses and experiments results, they find that a large portion of young married men in Saudi Arabia privately support women working outside the home.
+Importantly, these men greatly underestimate the proportion of support among other similar men [@MisperceivedSocialNorm].
+The study population is young married husbands aged 18 to 35 in Saudi Arabia.
+We aim to replicate the estimand that focuses on the effects of providing husbands with the true proportion of support.
 Their findings suggest that men who are given the actual proportion of their peers supporting WWOH are more likely to support their wives’ labor supply, and their wives are more likely to apply for job, attend interviews, be employed and enrol in driving lessons.
-Correcting misperceived beliefs manifests positive impacts on females, and the lack of communication emerges as a primary factor contributing to these misperceptions.
+Correcting misperceived beliefs yields positive impacts on females employment, and insufficient communication is associated with an increased likelihood of misperceptions [@MisperceivedSocialNorm].
 
@@
 
-## Bias and Weaknesses
+## Bias, Ethics and Weaknesses
+Throughout the survey and experiment, all participants granted permissions for the collection of data.
+After gathering information, the experimenters ensured that all responses remain confidential and anonymous, so the data we used for replication in this paper was also anonymous, with only the last three digits of their phone numbers retained.
+As a result, there are no ethical concerns during the process and in the paper.
+
 The authors, Leonardo Bursztyn, Alessandra L.
 González, and David Yanagizawa-Drott, implemented many modifications to the questions and weights in an attempt to minimize bias in the survey.
-However, it is acknowledged that bias is an inherent challenge when conducting experiments.
-The main experiment survey has a participant pool of 500 married men from Riyadh.
+However, it is acknowledged that bias is always a challenge when conducting experiments.
+The main experiment survey has a participant pool of 500 married men from Riyadh [@MisperceivedSocialNorm].
 Since Riyadh is the capital and the largest city in Saudi Arabia, the sample size might be relatively small and potentially biased.
-The reward offered, typically a five-dollar or twenty-dollar gift card, could be another factor contributing to potential biases considering the GDP in Saudi Arabia.
-The paper focuses on married men aged 18 to 35 with some level of education.
-It is noted that, for the majority of individuals, the expected age range for completing college or university education is between 20 and 24.
-Therefore, setting the age range from 18 to 35 might be a weakness in the experiment.
+Considering the economy in Saudi Arabia and Riyadh, the reward offered, typically a five-dollar or twenty-dollar gift card, could be another factor contributing to the weakness in both the original paper and our paper.
 
+The paper focuses on married men aged 18 to 35 with some level of post-secondary education.
+It is noted that the enrolment rate among students aged 20-24 in secondary program is relatively high in Saudi Arabia [@EducationGPS], so setting the age range from 18 to 35 might be a weakness in the experiment.
 There is a potential correlation between individuals who did not participate in the follow-up and those who do not support Women Working Outside the Home, also introducing the possibility of bias.
@@
 The authors mentioned that ‘expanding the scale and observing how information spreads in networks, and how it affects a large set of outcomes is an important topic for future work’ [@MisperceivedSocialNorm].
-Considering the potential biases and the experiment result stating correcting misperceived beliefs increase husbands’ support in WWOH, future research could greatly benefit from the extension of scale to enhance generalizability and actual effects on female employment in Saudi society.
+Considering the potential biases and the experiment result claiming that correcting misperceived beliefs increase husbands’ support in WWOH, future research could greatly benefit from the extension of scale to enhance generalizability and actual effects on female employment in Saudi society.
 
-Figure 9 in the original paper reveals that males who often engage in discussions about the WWOH exhibit perceived support only four percent smaller than the actual proportion.
-For those who rarely or very rarely discuss about the WWOH, their perceived support for WWOH is around forty percent smaller than the actual proportion.
+Figure 9 in the original paper reveals that males who often engage in discussions about the WWOH have perceived proportion of support only four percent smaller than the actual proportion.
+For those who rarely or very rarely discuss about the WWOH, their perceived proportion of support for WWOH is around forty percent smaller than the actual proportion.
 If the lack of communication facilitates misperceptions, one would expect a correlation between the frequency of communication and perceptions [@MisperceivedSocialNorm].
-Consequently, future studies could delve into strategies in preventing misperceived opinions from influencing social norms, and explore decision-making in the presence of collective misperceptions.
+Consequently, future studies could delve into strategies in preventing misperceived opinions from influencing social norms negatively, and explore decision-making in the presence of collective misperceptions.
 

### 2024-02-12 outputs/paper/paper.qmd
commit

--- 2024-02-12 outputs/paper/paper.qmd
@@
   pull(t_kn)
+
 # Other participants known standard deviation (%)
@@
   pull(t_mf)
+
 # Other participants with mutual friends standard deviation (%)
@@
 
+\newpage
 The the longer-term outcomes of the treatment are shown in @fig-3 with error bars indicating the 95% confidence intervals for these proportions.
@@
 There are two vertical lines that represent the actual proportion of respondents who agreed with the statement in @fig-national_survey_misperception, showing more than 80% of men underestimated the true proportion.
-The black line is for the control group, which reflects their perceptions about others' answers, and the red dashed line is for the treatment group, which reflects their perceptions about others' beliefs.
+The black line is for the control group and the red dashed line is for the treatment group.
+The lines reflect perceptions of participants about others' beliefs.
 The graph shows the support level of treatment group is mostly higher than control.

### 2024-02-12 outputs/paper/paper.qmd
discussion point 1

@@
 
-## First discussion point
+## Impact of Informational Intervention:
+
+The research findings have highlighted the importance of correcting misperceived social norms, not only to increase women's participation in the labor market but also to make progress in broader social norms and attitudes towards women's rights and autonomy.
+The study shows that interventions aimed at challenging and changing societal norms can have a significant impact on women's economic participation and social development.
+For instance, the study found that after an information intervention, more husbands were willing to sign up their wives for driving lessons, indicating a shift towards more progressive attitudes regarding women's mobility and independence.
+These changes can contribute to economic development by increasing the labor force and promoting gender equality.
+The researchers suggest that similar interventions could be effective in other contexts where misperceptions about social norms limit women's economic participation.
+This approach can offer valuable insights for policymakers and organizations aiming to promote gender equality and economic development, emphasizing the role of accurate information in challenging and changing societal norms.
+In summary, the study illustrates the significant impact of informational interventions in transforming social norms and behaviors, particularly in the context of gender roles and women's economic participation in Saudi Arabia.
+These insights can support women's rights and contribute to broader social and economic development goals.
 

### 2024-02-12 outputs/paper/paper.qmd
adding technology related discussion

@@
 This approach can offer valuable insights for policymakers and organizations aiming to promote gender equality and economic development, emphasizing the role of accurate information in challenging and changing societal norms.
-In summary, the study illustrates the significant impact of informational interventions in transforming social norms and behaviors, particularly in the context of gender roles and women's economic participation in Saudi Arabia.
-These insights can support women's rights and contribute to broader social and economic development goals.
+In today's world, digital platforms and social media hold a significant impact on the formation of public opinion and social norms.
+By making strategic use of these technologies, we can effectively disseminate accurate information and correct any misconceptions.
+We can leverage online platforms to share data on societal attitudes towards WWOH.
+This will enable interventions to reach a much wider audience, facilitating a more rapid and widespread change in perceptions.
 

### 2024-02-12 outputs/paper/paper.qmd
discussion point 2

@@
 
-## Impact of Informational Intervention:
+## 1. Impact of Informational Intervention:
 
@@
 
-## Second discussion point
+## 2. Broader Social Proof Implications
+
+It is possible to overcome harmful norms in cultural and societal settings by using social proof.
+
+One study @Counternormative found that communicating the increasing popularity of environmentally friendly behaviors encouraged individuals to adopt these behaviors themselves, demonstrating the power of social proof in effecting change in environmental contexts.
+This suggests that highlighting positive changes in societal behaviors can be effective in encouraging the adoption of new, more beneficial norms and practices, rather than focusing on static norms.
+
+Another study @OrganizedDiffusio has evaluated the impact of "organized diffusion" on community-based health and women's empowerment programs.
+This approach involves encouraging individuals who have received training or information to share it with others, thus spreading the benefits more widely.
+The study, which looked at programs in Mali, Nepal, and Nigeria, found that implementing this method can lead to significant changes in social norms without incurring additional costs.
+
+These studies show that by understanding and addressing specific normative beliefs underlying societal issues, policymakers and practitioners can design targeted interventions that utilize social proof effectively.
+By presenting evidence of changing norms and behaviors within a community, we can foster a more inclusive, equitable, and sustainable society.
+
+Integrating these studies enhances our understanding of how social proof can be applied across different issues and cultural contexts to promote positive social change.
 

### 2024-02-12 outputs/paper/paper.qmd
reference
finish all parts in the paper

@@
 thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia.
-Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1461/"
+Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1557/"
 date: "February 12, 2024"
@@
 # Discussion
-
-## 1. Impact of Informational Intervention:
-
+## Impact of Informational Intervention: 
 The research findings have highlighted the importance of correcting misperceived social norms, not only to increase women's participation in the labor market but also to make progress in broader social norms and attitudes towards women's rights and autonomy.
@@
 
-## 2. Broader Social Proof Implications
-
+## Broader Social Proof Implications
 It is possible to overcome harmful norms in cultural and societal settings by using social proof.
@@
 
-## Third discussion point
+## Inverse Pattern of Saudi female labor force participation rate during pandemic
+According to the Gender Data Portal from The World Bank, the global average male labor force participation had a decrease of 1.6%, reaching 58.6% in 2020, followed by a rebound to 59.5% in 2021.
+In fact, this trend was observed across various countries, irrespective of gender.
+
+For example, the Canadian female labor force participation rates in 2019, 2020 and 2021 were 61.4%, 59.5%, 60.6%, respectively, and the Canadian male labor force participation rates for the same years were 70.1%, 68.6%, 69.6%.
+A similar pattern is discernible in India, where the female labor force participation rates in 2019, 2020 and 2021 were 23.7%, 22.7%, 23%, while corresponding male rates stood at 73.6%, 72.3%, 72.7% [@worldbankLaborForce].
+
+Interestingly, Saudi Arabia exhibited an inverse pattern.
+While the Saudi male labor force participation rate remained relatively stable, the female rate, along with that of the United Arab Emirates, increased in 2020 and then decreased in 2021.
+To be more specific, the Saudi female labor force participation rate had a notable increase of 4.9% (nearly one-fifth of the total), reaching 29.5% in 2020, and then declining to 27.8% in 2021.
+Similarly, female rate in United Arab Emirates increased by 4.2% to 61% in 2020, but decreased to 52.8% in 2021 [@worldbankLaborForce].
+
+The observed fluctuation in world labor force participation rates, particularly Saudi Arabia, leads to speculation on the underlying factors driving these trends.
+The impact of quarantine is a significant factor, as individuals working from home remained mostly unaffected, unlike those in traditional office settings.
+This is likely the reason behind the abnormal employment pattern among Saudi women at the start of the pandemic.
+Moreover, the contrasting pattern in Saudi female labor force participation rate, compared to the world trend, highlights the phenomenon  that many employed females tend to work at home, either willingly or due to traditional social norms.
+The 2020 surge could indicate potential willingness among Saudi women to explore employment opportunities.
 

### 2024-02-12 outputs/paper/paper.qmd
include abstract

@@
 thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia.
-Replication on Social Science Reproduction platform available at: https://www.socialsciencereproduction.org/reproductions/1557/"
+Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/"
 date: "February 12, 2024"
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia.
+Bursztyn, González, and Yanagizawa-Drott explore this social norm through surveys, experiments and visualizations, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men, and correcting this misperception increases husbands’ willingness to help wives search for jobs.
+This paper replicates the data from their study to analyze young husbands’ actual opinions and perceptions, confirming similar findings.
+This paper also discusses strategies for reducing misperceptions and the unusual Saudi female employment rate during the pandemic."
 format: pdf
@@
 We seek to replicate two claims, (1) There is a wedge between the actual and perceived proportion of men supporting women working outside the home, and (2) Most Saudi men who privately support WWOH fail to understand that others do as well, and they are more likely to help their wives find jobs when they know the actual portion of men supporting WWOH.
-The experiments and surveys results we will try to replicate are (1) the actual portion of support of WWOH from young husbands, (2) the existence of misperception, and (3) the effects of correcting beliefs on wives in Saudi Arabia.
+The experiments and surveys results we will try to replicate are (1) the actual portion of support of WWOH from young husbands, (2) the existence of misperception, and (3) the effects of correcting beliefs on female employment in Saudi Arabia.
 Our reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr].
@@
 After that, we will create a reproduction of the selected results to verify their data and their findings based on the data.
-In the last section, we will discuss our findings, including ….
-We will also conclude potential bias and weaknesses, as well as a push for future research
+In the last section, we will discuss the impact of informational intervention, the use of social proof to overcome harmful norms, and the inverse pattern of female labor force participation rate in Saudi Arabia during the pandemic.
+We will also conclude ethics, potential bias, and weaknesses topics, as well as a push for future research.
 

### 2024-02-12 outputs/paper/paper.qmd
include simulation

@@
 install.packages('kableExtra')
+install.packages('tidyverse')
 ```
@@
 library(kableExtra)
+library(tidyverse)
 ```
@@
 The experiments and surveys results we will try to replicate are (1) the actual portion of support of WWOH from young husbands, (2) the existence of misperception, and (3) the effects of correcting beliefs on female employment in Saudi Arabia.
-Our reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr].
+Our reproduction used the programming language R [@r], the analysis used the following packages: Haven[@rHaven], Dplyr [@rDplyr], Ggplot2 [@rGgplot2], Readr [@rReadr], Here [@rHere], Janitor [@rJanitor], KableExtra [@rKableExtra], Knitr [@rKnitr], Tidyverse [@rTidyverse].
 

### 2024-02-12 scripts/00-simulation.R

@@ -3,3 +3,77 @@
 # Authors: Boxuan Yi, Ruoxian Wu
 # Pre-requisites: none
 
+# Load Packages
+library(tidyverse)
+library(janitor)
+library(knitr)
+
+# Simulation for three surveys
+# Simulation for the main experiment
+set.seed(1232)
+condition <- c("0", "1")
+simulated_main_exp <-
+  tibble("Condition2" = sample(condition, 500, replace = TRUE),
+         "Age" = sample(18:35, 500, replace = TRUE),
+         "College_deg" = sample(0:1, 500, replace = TRUE),
+         "employed_now" = sample(0:1, 500, replace = TRUE),
+         "employed_wife" = sample(0:1, 500, replace = TRUE),
+         "children" = sample(0:12, 500, replace = TRUE),
+         "mwage_self" = sample(0:1, 500, replace = TRUE),
+         "mwage_others" = sample(0:29, 500, replace = TRUE),
+         "mwage_confidence" = sample(1:5, 500, replace = TRUE),
+         "outside_self" = sample(0:1, 500, replace = TRUE),
+         "outside_others" = sample(0:29, 500, replace = TRUE),
+         "outside_confidence" = sample(1:5, 500, replace = TRUE),
+         "semiseg_self" = sample(0:1, 500, replace = TRUE),
+         "semiseg_others" = sample(0:29, 500, replace = TRUE), 
+         "semiseg_confidence" = sample(1:5, 500, replace = TRUE),
+         'labor_demand_guess' = sample(0:100, 500, replace = TRUE),
+         'signed_up_number' = sample(0:1, 500, replace = TRUE),
+         'outside_guess' = sample(0:30, 500, replace = TRUE),
+         'semiseg_guess' = sample(0:30, 500, replace = TRUE),
+         'mwage_guess' = sample(0:30, 500, replace = TRUE)) |> kable()
+simulated_main_exp
+
+# Simulation for the follow-up
+simulated_follow_up <-
+  tibble(
+    "Condition2" = sample(condition, 500, replace = TRUE),
+    "Age" = sample(18:35, 500, replace = TRUE),
+    "College_deg" = sample(0:1, 500, replace = TRUE),
+    "employed_now" = sample(0:1, 500, replace = TRUE),
+    "employed_wife" = sample(0:1, 500, replace = TRUE),
+    "children" = sample(0:12, 500, replace = TRUE),
[…]

### 2024-02-12 outputs/paper/paper.qmd
modify figure 1

@@
 ```{r}
-#| label: fig-1
-#| fig-cap: Histogram of Perceptual Gaps in Beliefs About Women Working Outside the Home
+#| label: fig-wedge
+#| fig-cap: Wedges in Perceptions of Others’ Beliefs (Main Experiment)
 #| echo: false
@@
 
-# Plotting a histogram of the wedge share
-f2 <- ggplot(df, aes(x = .data[[paste0(q, "_wedge_share")]])) +
-  geom_histogram(binwidth = 10.5, fill = "lightgrey", color = "black") + 
-  scale_x_continuous("Wedge (guess % - objective %)", 
-                     breaks = seq(-100, 100, by = 20), 
-                     limits = c(-100, 100), 
-                     expand = c(0.1, 0.5)) +
-  scale_y_continuous("Density", expand = c(0.5, 0)) +
-  geom_vline(xintercept = 0, linetype = "dashed", color = "#FF4136", size = 0.5) + # Less prominent zero line
-  labs(title = "Distribution of Wedge (Guess % - Objective %)", # Add a title
-       caption = "Red dashed line represents the zero point") + # Add a caption
-  theme_minimal(base_size = 12) + 
-  theme(
-    plot.background = element_blank(),
-    panel.background = element_rect(fill = "white", colour = "black"), 
-    axis.text = element_text(size = 12, color = "black"), 
-    axis.title = element_text(size = 14, color = "black"),
-    panel.grid.major = element_line(color = "lightgrey", size = 0.2), 
-    panel.grid.minor = element_blank(),
-    plot.title = element_text(hjust = 0.5), 
-    plot.caption = element_text(hjust = 0.5) 
-  )
+f2 <- df |> ggplot(aes(x = (outside_wedge/30) * 100))+
+  geom_histogram(aes(y = after_stat(density)), bins = 20, fill = "grey", color = "black", na.rm = TRUE, breaks = seq(-100, 30, by = 10)) +   
+  geom_vline(xintercept = 0, color = "red4", linetype = "dashed") +
+  theme_minimal() +
+  scale_x_continuous(name= "Wedge (guess% - objective %)", 
+                     breaks = c(-100,-80,-60,-40,-20,0,20,40,60,80,100), 
+                     limits = c(-100,100)) +
+  scale_y_continuous(name = "Density", 
+                     breaks = c(0, 0.005, 0.01, 0.015),
+                     limits = c(0, 0.015))
+
 f2
 ```
-
 The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
@@
 We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
-@fig-1 specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
+@fig-wedge specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
 It was found that more than half of participants underestimated the support for WWOH.
@@
 #| echo: false
+#| warning: false
 #| label: tbl-summary_table
@@
 #| echo: false
+#| warning: false
 #| label: fig-national_survey_misperception

### 2024-02-13 outputs/paper/paper.qmd
modify figure1

@@
 ```
+
 The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
@@
 p_value_driving <- t.test(driving_fl ~ factor(condition), data = df_filtered, na.rm = TRUE)$p.value
-
 ```

### 2024-02-13 r_code/Figure2.R
save figure 1

@@ -20,30 +20,23 @@ q_self_mean <- mean(df[[paste0(q, "_self")]], na.rm = TRUE)
 df[[paste0(q, "_wedge_share")]] <- (df[[paste0(q, "_wedge")]] / 30) * 100
 
 # Plotting a histogram of the wedge share
-f2 <- ggplot(df, aes(x = .data[[paste0(q, "_wedge_share")]])) +
-  geom_histogram(binwidth = 10.5, fill = "lightgrey", color = "black") + # Adjust fill for contrast
-  scale_x_continuous("Wedge (guess % - objective %)", 
-                     breaks = seq(-100, 100, by = 10), 
-                     limits = c(-100, 100), # Explicitly set x-axis limits
-                     expand = c(0, 0.5)) +
-  scale_y_continuous("Density", expand = c(0.5, 0)) +
-  geom_vline(xintercept = 0, linetype = "dashed", color = "#FF4136", size = 0.5) + # Less prominent zero line
-  labs(title = "Distribution of Wedge (Guess % - Objective %)", # Add a title
-       caption = "Red dashed line represents the zero point") + # Add a caption
-  theme_minimal(base_size = 12) + # Use theme_minimal with a base font size
-  theme(
-    plot.background = element_blank(),
-    panel.background = element_rect(fill = "white", colour = "black"), # White background with border
-    axis.text = element_text(size = 12, color = "black"), # Ensure text is black for readability
-    axis.title = element_text(size = 14, color = "black"),
-    panel.grid.major = element_line(color = "lightgrey", size = 0.2), # Subtle gridlines
-    panel.grid.minor = element_blank(),
-    plot.title = element_text(hjust = 0.5), # Center the title
-    plot.caption = element_text(hjust = 0.5) # Center the caption
-  )
+
+f2 <- df |> ggplot(aes(x = (outside_wedge/30) * 100))+
+  geom_histogram(aes(y = after_stat(density)), bins = 20, 
+                 fill = "grey", 
+                 color = "black", 
+                 na.rm = TRUE, 
+                 breaks = seq(-100, 30, by = 10)) +   
+  geom_vline(xintercept = 0, color = "red4", linetype = "dashed") +
+  theme_minimal() +
+  scale_x_continuous(name= "Wedge (guess% - objective %)", 
+                     breaks = c(-100,-80,-60,-40,-20,0,20,40,60,80,100), 
+                     limits = c(-100,100)) +
[…]

### 2024-02-13 scripts/01-test.R
test

@@ -2,3 +2,73 @@
 # Purpose: Testing datasets
 # Author: Boxuan Yi, Ruoxian Wu
 
+
+library(haven)
+
+## Raw data test
+
+# Data path
+datadir <- "/cloud/project/inputs/data/"
+raw_data_path <- file.path(datadir, "raw_data/01_main_exp_raw1.dta")
+
+# Read the data file
+df <- read_dta(raw_data_path)
+
+
+## Missing data test
+
+# Calculate the number of missing values per column
+missing_values <- sapply(df, function(x) sum(is.na(x)))
+
+# Print missing values
+print(missing_values)
+
+## Distribution Test for Key Variables
+
+# Numerical variables
+numerical_stats <- summary(df[c("employed_ever", "employed_now", "employed_wife", "num_mutual_friends")])
+
+print(numerical_stats)
+
+# Categorical variables
+marital_distribution <- table(df$marital)
+education_distribution <- table(df$education)
+employed_ever_distribution <- table(df$employed_ever)
+
+print(marital_distribution)
+print(education_distribution)
+print(employed_ever_distribution)
+
+## clean data test
+
+# Data path
+datadir_clean <- "/cloud/project/inputs/data/"
+clean_data_path <- file.path(datadir, "clean_data/01_main_exp_clean.dta")
+
+# Read the data file
+df2 <- read_dta(clean_data_path)
+
+
+## Missing data test
+
+# Calculate the number of missing values per column
+missing_values <- sapply(df2, function(x) sum(is.na(x)))
+
+# Print missing values
+print(missing_values)
+
+## Distribution Test for Key Variables
+
+# Numerical variables
+numerical_stats <- summary(df2[c("employed_now", "employed_wife", "labor_demand_guess", "signed_up_number")])
+
+print(numerical_stats)
+
+# Categorical variables
+marital_distribution <- table(df$marital)
+education_distribution <- table(df$education)
+employed_ever_distribution <- table(df$employed_ever)
+
+print(marital_distribution)
+print(education_distribution)
+print(employed_ever_distribution)

### 2024-02-13 outputs/paper/paper.qmd
Change Table 1 result description

@@
 
-By using the regression analysis, we examine the treatment effect on the participants' likelihood to sign up for a job matching service for their wives.
-The treatment variable is significant across all model specifications, with coefficients ranging from 0.0853 to 0.0899.
-The constant term varies considerably across different model specifications, suggesting differing baseline propensities for signing up absent the treatment.
-The p-values for the treatment effect, under various robustness checks such as robust standard errors, wild bootstrap, and permutation test, all indicate significance, ranging from 0.008 to 0.038.
-These results reinforcing the treatment's positive impact on sign-up rates (@tbl-summary_table).
+@tbl-summary_table presents the successful randomization in the experiment, which is evident from the comparable statistics between the treatment and control groups.
+For instance, both groups have almost identical average age, with the control group at 24.64 years and the treatment group at 24.91 years.
+Similarly, the employment rates are also similar, with 87.45% employed in the control group as compared to 85.77% in the treatment group.
+Additionally, the percentage of participants with a college degree is also balanced, with 55.06% in the control group and 57.31% in the treatment group.
+These figures imply that any differences in the intervention outcomes can be confidently attributed to the treatment itself rather than to underlying demographic differences.
 
@@
 
-Another study @OrganizedDiffusio has evaluated the impact of "organized diffusion" on community-based health and women's empowerment programs.
+Another study @OrganizedDiffusion has evaluated the impact of "organized diffusion" on community-based health and women's empowerment programs.
 This approach involves encouraging individuals who have received training or information to share it with others, thus spreading the benefits more widely.

### 2024-02-13 scripts/01-test.R
modify tests

@@ -2,8 +2,44 @@
 # Purpose: Testing datasets
 # Author: Boxuan Yi, Ruoxian Wu
 
-
+library(dplyr)
 library(haven)
+## Clean data test
+main_clean <- read_dta(here("inputs/data/01_main_exp_clean_original.dta"))
+follow_up_clean <- read_dta(here("inputs/data/02_follow_up_clean_original.dta"))
+online_survey_clean <- read_dta(here("inputs/data/03_1st_online_svy_clean_original.dta"))
+
+# Main experiment dataset tests
+length(unique(main_clean$condition2)) == 2
+main_clean$age |> unique()
+main_clean$education |> max() <= 9
+main_clean$education |> min() >= 1
+main_clean$outside_confidence |> max() <= 5
+main_clean$outside_wedge |> min() >= -29
+main_clean$outside_wedge |> min() <= 29
+length(unique(main_clean$signed_up_number)) == 2
+length(unique(main_clean$employed_wife)) == 2
+
+# Follow-up tests
+length(unique(follow_up_clean$employed_now)) == 2
+length(unique(follow_up_clean$college_deg)) == 2
+follow_up_clean |> filter(employed_wife == 1) |> nrow()
+
+wife_outside3mos_num <- follow_up_clean |> filter(employed_3mos_out_fl == 1) |> nrow()
+wife_3mos_num <- follow_up_clean |> filter(employed_wife == 1) |> nrow()
+wife_outside3mos_num <= wife_3mos_num
+
+# Online survey tests
+online_survey_clean |> filter(condition == 0) |> nrow()
+online_survey_clean |> filter(!is.na(c_list)) |> nrow()
+online_survey_clean |> filter(!is.na(c_outside_self)) |> nrow()
+online_survey_clean |> filter(!is.na(c_outside_wedge)) |> nrow()
+
+online_survey_clean |> filter(condition == 1) |> nrow()
+online_survey_clean |> filter(!is.na(t_outside_confidence)) |> nrow()
+online_survey_clean |> filter(!is.na(t_outside_guess_frac)) |> nrow()
+online_survey_clean |> filter(!is.na(t_outside_guess)) |> nrow()
+
 
 ## Raw data test
 

### 2024-02-13 outputs/paper/paper.qmd
change result delete "author"

@@
 
-The authors calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
+We calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
 The negative wedge indicates that the participant underestimated the support for WWOH.
@@
 
-The authors, Leonardo Bursztyn, Alessandra L.
-González, and David Yanagizawa-Drott, implemented many modifications to the questions and weights in an attempt to minimize bias in the survey.
+We implemented many modifications to the questions and weights in an attempt to minimize bias in the survey.
 However, it is acknowledged that bias is always a challenge when conducting experiments.
-The main experiment survey has a participant pool of 500 married men from Riyadh [@MisperceivedSocialNorm].
+The main experiment survey has a participant pool of 500 married men from Riyadh.
 Since Riyadh is the capital and the largest city in Saudi Arabia, the sample size might be relatively small and potentially biased.
@@
 Although there is a customary practice of husbands' guardianship with decision-making authority in Saudi Arabia, gaining insights into the opinions of Saudi women regarding employment and working outside the home is essential for future study.
-The authors mentioned that ‘expanding the scale and observing how information spreads in networks, and how it affects a large set of outcomes is an important topic for future work’ [@MisperceivedSocialNorm].
+The original paper mentioned that ‘expanding the scale and observing how information spreads in networks, and how it affects a large set of outcomes is an important topic for future work’ [@MisperceivedSocialNorm].
 Considering the potential biases and the experiment result claiming that correcting misperceived beliefs increase husbands’ support in WWOH, future research could greatly benefit from the extension of scale to enhance generalizability and actual effects on female employment in Saudi society.
 
-Figure 9 in the original paper reveals that males who often engage in discussions about the WWOH have perceived proportion of support only four percent smaller than the actual proportion.
+In the original paper reveals that males who often engage in discussions about the WWOH have perceived proportion of support only four percent smaller than the actual proportion.
 For those who rarely or very rarely discuss about the WWOH, their perceived proportion of support for WWOH is around forty percent smaller than the actual proportion.

### 2024-02-13 outputs/paper/paper.qmd
pdf layout

@@
 # Results
+We calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
+The negative wedge indicates that the participant underestimated the support for WWOH.
+Conversely, a positive wedge suggests that the participant overestimated the support for WWOH.
+We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
+@fig-wedge specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
+It was found that more than half of participants underestimated the support for WWOH.
+There is a clear gap between perceived and actual social norms regarding women's work outside the home.
+The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.
+
 ```{r}
@@
 ```
-
-We calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
-The negative wedge indicates that the participant underestimated the support for WWOH.
-Conversely, a positive wedge suggests that the participant overestimated the support for WWOH.
-We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
-@fig-wedge specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
-It was found that more than half of participants underestimated the support for WWOH.
-There is a clear gap between perceived and actual social norms regarding women's work outside the home.
-The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.
-
+\newpage
 @tbl-summary_table presents the successful randomization in the experiment, which is evident from the comparable statistics between the treatment and control groups.
@@
 
-\newpage
 @fig-national_survey_misperception is made to illustrate the result of the first national survey.

### 2024-02-13 outputs/paper/paper.qmd
improve our writing

@@
 The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials.
+The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975
 
@@
 # Results
-We calculated "wedges" which represent the difference between what participants guessed and the actual percentage of agreement among their session peers regarding women working outside the home (WWOH).
-The negative wedge indicates that the participant underestimated the support for WWOH.
-Conversely, a positive wedge suggests that the participant overestimated the support for WWOH.
-We replicate the histograms to check the distribution of the wedges between participants' beliefs about the support for WWOH among their session participants and the actual levels of support.
-@fig-wedge specifically maps the distribution of these "wedges" -- the differences between each participant's guess and the actual percentage of session participants who agreed with the pro-WWOH statement.
-It was found that more than half of participants underestimated the support for WWOH.
+In the main experiment, the “wedge” in @fig-wedge is calculated as ‘participant’s guess about the percent of session participants agreeing with the pro-WWOH statement’ minus ‘actual percent of session participants agreeing with the pro-WWOH statement’.
+A negative wedge indicates that the participant underestimate the support for WWOH, while a positive wedge suggests that the participant overestimate the support.
+The red dashed vertical line represents a wedge of 0, showing a correct guess of the proportion.
+From the distribution of @fig-wedge, 71.8% of participants underestimate the support for WWOH among session participants, with an average wedge of -24.1%, even though these individuals were recruited from the same neighbourhoods and knew an average of 15 out of 29 people in the session.
 There is a clear gap between perceived and actual social norms regarding women's work outside the home.
-The left skew of the histogram would indicate that a majority of participants underestimated the true level of support for WWOH.
 
@@
 ```
+
+```{r}
+#| include: false
+# Calculate actual measurement
+mean(main_clean$num_know_per)
+mean(main_clean$outside_wedge)/30
+num_underestimate <- main_clean |> filter(outside_wedge < 0) |> nrow()
+total_num_participant <-  main_clean |> nrow()
+num_underestimate / total_num_participant
+```
+
 \newpage
-@tbl-summary_table presents the successful randomization in the experiment, which is evident from the comparable statistics between the treatment and control groups.
-For instance, both groups have almost identical average age, with the control group at 24.64 years and the treatment group at 24.91 years.
-Similarly, the employment rates are also similar, with 87.45% employed in the control group as compared to 85.77% in the treatment group.
-Additionally, the percentage of participants with a college degree is also balanced, with 55.06% in the control group and 57.31% in the treatment group.
-These figures imply that any differences in the intervention outcomes can be confidently attributed to the treatment itself rather than to underlying demographic differences.
+Before discussing the results concluded from experimental intervention, @tbl-summary_table presents a summary of features of the groups - control group and treatment group, as well as all participant as a group.
+As mentioned in Section 2, 500 participants are randomly assigned to either the control group or treatment group.
+According to @tbl-summary_table, we can infer from the comparable statistics that the randomization in the experiment is successful, with individual characteristics balanced in all three groups.
+For instance, all groups have a similar average age, with the control group at 24.64 years and the treatment group at 24.91 years.
+Employment rates are also on the same level, with 87.45% in the control group compared to 85.77% in the treatment group.
+Each number in parentheses is the p-value of the row above.
 
@@
 
-@fig-job_sign_up illustrates the difference in job matching service sign-up rates between the control and treatment groups.
-The bar for the treatment group would be higher than the control group's, showing a clear increase in the likelihood of signing up due to the treatment.
-The specific values of 23.48% for the control group and 32.02% for the treatment group, along with a p-value of 0.0424, would be represented, indicating a statistically significant effect of the information intervention on the participants' actions.
+@fig-job_sign_up displays the main result from the experimental intervention, illustrating the difference in job matching service sign-up rates between the control and treatment groups.
+In the control group, 23.48% of participants are willing to sign up their wives for the job service when provided with another gift card option.
+In the treatment group, where participants are given the actual proportion of support for WWOH, 32.02% of the respondents prefer to sign up their wives for the job service, which is a 32% increase (with a p-value of 0.0424).
 
-The combination of @tbl-summary_table and @fig-job_sign_up demonstrates the efficacy of the information treatment in altering the participants' behavior towards women's labor market participation, revealing not only a statistical significance but also practical importance in the context of social norms and labor supply outcomes in Saudi Arabia.
+The combination of @tbl-summary_table and @fig-job_sign_up demonstrates the effects of the information intervention on participants’ behavior and opinions towards women's labor market participation, revealing not only a statistical significance but also practical importance in the context of social norms and labor supply outcomes in Saudi Arabia.
 
 \newpage
-The the longer-term outcomes of the treatment are shown in @fig-3 with error bars indicating the 95% confidence intervals for these proportions.
+The longer-term outcomes of the experiment on information intervention are shown in @fig-3 with error bars indicating the 95% confidence intervals for these proportions.
 
-The job matching service sign-up rates is presented in @fig-3 a.
-In the control group, 6.04% of participants chose to sign their wives up for the job service instead of taking a gift card payment while 16.74% participants in the treatment group chose the job service (p-value = 0.001).
-The increased sign-up rate in the treatment group more young men accepted the idea of WWOH after the correction of misperceptions.
+The percentage of wives applying for a job outside the home is presented in @fig-3 a.
+In the control group, 6.04% of wives apply for jobs outside, while 16.74% wives in the treatment group choose to do so.
+The increase in application rate is quite obvious, nearly a 180% increase with a p-value of 0.001.
+@fig-3 b shows the impact of the informational intervention on outside-home job interviews.
+The interview rate in the control group is 1.1% while the treatment group has 5.95%, with p-value of 0.013.
+Both @fig-3 a and @fig-3 b display significant increases.
 
-In @fig-3 b, the informational intervention has impact on participants' wives were interviewed for a job outside the home.
-After the intervention, there was a statistically significant increase in interviews, with the percentage of wives who interviewed for a job outside the home rising from 1.1% to 5.95%.
-This more than fivefold increase (p-value = 0.013) suggests that the treatment had a notable effect on the interview rates for jobs outside the home.
+Regarding the employment rates for this kind of job, @fig-3 c shows that the employment rate increases from 7.69% to 9.73%.
+Although this indicates an increase, it is not statistically significant (p-value = 0.456), implying that though the intervention might have had an encouraging effect on job-seeking behavior, it does not translate into a significant difference in actual employment within the study period.
 
-Similarly, the informational intervention effects on the employment rate of participants' wives in jobs outside the home according to @fig-3 c.
-The employment rate post-intervention increased from 7.69% to 9.73%.
-Although this represents an increase, it is not statistically significant (p-value = 0.456), implying that while the intervention might have had an encouraging effect on job-seeking behavior, it did not translate into a significant difference in actual employment within the study period.
+To further explore the long-term influence, @fig-3 d shows the share of husbands who report in a hypothetical question whether they would sign their wives up for driving lessons.
+The control group has a rate of 68.13%, and the treatment group has a rate of 78.38%, with p-value as 0.03.
+The increase in husbands’ willingness to sign their wives up for driving lessons implies that correcting misperception influences beyond behaviours associated with female employment, creating potential impacts on broader social norms and attitudes toward women's conditions in Saudi Arabia.
 
-Besides, @fig-3 d indicates that the change in husbands' willingness to sign their wives up for driving lessons as a result of the informational intervention.
-There is a significant increase from 68.13% to 78.38% in the proportion of husbands who reported they would sign their wives up for driving lessons (p-value = 0.03).
-This result indicates that the informational intervention not only had an impact on labor supply outcomes but also potentially affected broader social norms and attitudes toward women's rights and autonomy in Saudi Arabia, as evidenced by the increased openness to women's mobility through driving.
-
-Overall, the treatment has a significant impact on both immediate and longer-term outcomes related to women's labor market participation and related behaviors (@fig-3).
+Overall, the treatment has a significant effects on both immediate and longer-term outcomes related to women labor market participation based on @fig-3.
 
@@
 
-@fig-national_survey_misperception is made to illustrate the result of the first national survey.
-There are two vertical lines that represent the actual proportion of respondents who agreed with the statement in @fig-national_survey_misperception, showing more than 80% of men underestimated the true proportion.
-The black line is for the control group and the red dashed line is for the treatment group.
-The lines reflect perceptions of participants about others' beliefs.
-The graph shows the support level of treatment group is mostly higher than control.
-This figure underscores a significant discrepancy between personal beliefs and perceived societal norms.
-The larger sample size of this national survey strengthens the evidence that men privately support women's employment outside the home more than they assume others do, suggesting widespread misperceptions about societal norms.
+@fig-national_survey_misperception is created to illustrate the results of the national survey conducted with 1460 Saudi men aged from 18 to 35.
+The x-axis represents the share of others agreeing, and the y-axis denotes the cumulative probability that participants agree with the pro-WWOH statement.
+Two vertical lines in @fig-national_survey_misperception represent the actual proportion of respondents who agree with the statement.
+
+There is no significant difference between the data concerning the control group and the treatment group.
+@fig-national_survey_misperception reveals that the average proportion of support for both groups is slightly above 80%, while more than 90% of men underestimate this proportion.
+The number of underestimations is larger than the number observed in the main experiment, and one explanation is that participants are no longer being asked about opinions from people that they are familiar.
+
+This figure, once again, underscores the discrepancy between personal beliefs and perceived societal norms.
+The larger sample size of this national survey also bolsters the evidence that men privately support women's employment outside the home more than they assume others do, suggesting widespread misperceptions in current Saudi society.
 

### 2024-02-13 outputs/paper/paper.qmd
modify figure 4(original)

@@
 #| label: fig-3
-#| fig-cap: Histogram of Perceptual Gaps in Beliefs About Women Working Outside the Home
+#| fig-cap: Long-Term Labor Supply Outcomes (Follow-Up)
 #| echo: false
@@
   annotate("text", x = 1, y = max(df_stats$applied_rate_hi) + 3, label = paste("p-value =", round(p_value_applied, 3)), size = 4) +
-  labs(x = "", y = "% Applied", title = "Long-Term Labor Supply Outcomes") +
+  labs(x = "", y = "Percent", title = "Applied for job") +
   theme_minimal() +
@@
   annotate("text", x = 1.5, y = max(df_stats$interviewed_rate_hi) + 5, label = paste("p-value =", round(p_value_interviewed, 3)), size = 4) +
-  labs(y = "% Interviewed", x = "") +
+  labs(y = "Percent", x = "") +
   theme_minimal() +
@@
   annotate("text", x = 1.5, y = max(df_stats$employed_now_rate_hi) + 5, label = paste("p-value =", round(p_value_employed_now, 3)), size = 4) +
-  labs(y = "% Employed Now", x = "") +
+  labs(y = "Percent", x = "") +
   theme_minimal() +
@@
   annotate("text", x = 1.5, y = max(df_stats$driving_rate_hi) + 5, label = paste("p-value =", round(p_value_driving, 3)), size = 4) +
-  labs(y = "% Driving", x = "Condition") +
+  labs(y = "Percent", x = "Condition") +
   theme_minimal() +

### 2024-02-13 outputs/paper/paper.qmd
improve figures

@@
 #| layout-ncol: 2
-#| fig-subcap: ["Applied Rate","Interviewed Rate", "Employed Now Rate", "Driving Rate"]
+#| fig-subcap: ["Applied Rate", "Interviewed Rate", "Employed Now Rate", "Driving Rate"]
 
@@
   annotate("text", x = 1, y = max(df_stats$applied_rate_hi) + 3, label = paste("p-value =", round(p_value_applied, 3)), size = 4) +
-  labs(x = "", y = "Percent", title = "Applied for job") +
+  labs(x = "", y = "Percent", title = "Panel A. Applied for job") +
   theme_minimal() +
@@
   annotate("text", x = 1.5, y = max(df_stats$interviewed_rate_hi) + 5, label = paste("p-value =", round(p_value_interviewed, 3)), size = 4) +
-  labs(y = "Percent", x = "") +
+  labs(y = "Percent", x = "", title = "Panel B. Interviewed for job") +
   theme_minimal() +
@@
   annotate("text", x = 1.5, y = max(df_stats$employed_now_rate_hi) + 5, label = paste("p-value =", round(p_value_employed_now, 3)), size = 4) +
-  labs(y = "Percent", x = "") +
+  labs(y = "Percent", x = "", title = "Panel C. Employed") +
   theme_minimal() +
@@
   annotate("text", x = 1.5, y = max(df_stats$driving_rate_hi) + 5, label = paste("p-value =", round(p_value_driving, 3)), size = 4) +
-  labs(y = "Percent", x = "Condition") +
+  labs(y = "Percent", x = "", title = "Panel D. Driving lessons") +
   theme_minimal() +

### 2024-02-13 outputs/paper/paper.qmd
improve based on peer review

@@
 ---
-
-```{r}
-#| message: false
-#| echo: false
-# Install packages we need
-install.packages('haven')
-install.packages('dplyr')
-install.packages('ggplot2')
-install.packages('readr')
-install.packages('here')
-install.packages('janitor')
-install.packages('knitr')
-install.packages('kableExtra')
-install.packages('tidyverse')
-```
 

### 2024-02-13 scripts/00-simulation.R

@@ -3,6 +3,17 @@
 # Authors: Boxuan Yi, Ruoxian Wu
 # Pre-requisites: none
 
+# Install packages we need
+install.packages('haven')
+install.packages('dplyr')
+install.packages('ggplot2')
+install.packages('readr')
+install.packages('here')
+install.packages('janitor')
+install.packages('knitr')
+install.packages('kableExtra')
+install.packages('tidyverse')
+
 # Load Packages
 library(tidyverse)
 library(janitor)

### 2024-02-13 scripts/01-test.R

@@ -1,6 +1,7 @@
 #### Preamble ####
 # Purpose: Testing datasets
 # Author: Boxuan Yi, Ruoxian Wu
+# Prerequest: none
 
 library(dplyr)
 library(haven)
@@ -42,14 +43,12 @@ online_survey_clean |> filter(!is.na(t_outside_guess)) |> nrow()
 
 
 ## Raw data test
-
 # Data path
 datadir <- "/cloud/project/inputs/data/"
 raw_data_path <- file.path(datadir, "raw_data/01_main_exp_raw1.dta")
 
 # Read the data file
 df <- read_dta(raw_data_path)
-
 
 ## Missing data test
 

### 2024-02-13 scripts/02-download.R

@@ -2,5 +2,5 @@
 # Purpose: Downloads and saves survey data
 # Author: Boxuan Yi, Ruoxian Wu
 
-# We downloaded our data from https://www.aeaweb.org/articles?id=10.1257/aer.20180975 and
-# from its replicated package https://www.openicpsr.org/openicpsr/project/119404/version/V1/view
+# We manually downloaded our data from https://www.aeaweb.org/articles?id=10.1257/aer.20180975 and
+# from its replicated package https://www.openicpsr.org/openicpsr/project/119404/version/V1/view 

### 2024-02-14 outputs/paper/paper.qmd
modify abstract

@@
 abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia.
-Bursztyn, González, and Yanagizawa-Drott explore this social norm through surveys, experiments and visualizations, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men, and correcting this misperception increases husbands’ willingness to help wives search for jobs.
-This paper replicates the data from their study to analyze young husbands’ actual opinions and perceptions, confirming similar findings.
-This paper also discusses strategies for reducing misperceptions and the unusual Saudi female employment rate during the pandemic."
+We use data and surveys from the American Economic Association to analyze this perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men.
+This paper also discusses the positive effects brought about by correcting this misperception, strategies for reducing information intervention, and the unusual Saudi female employment rate during the pandemic."
 format: pdf
@@
 Barriers to the employment of women exert a significant influence on female labor, presenting a constraint to increasing economic opportunities for women [@sciencedirectOrganizationalEconomic].
-Saudi Arabia is a recognizable example of a country with a low rate of female labor force participation.
+Saudi Arabia is an example of a country with a low rate of female labor force participation.
 In 2022, the female labor force participation rate, defined as the percentage of the female population aged 15 and above that is employed, is only 27.8% in Saudi Arabia.
@@
 
+The variables from the main experiment dataset that we will use are condition2 (control or treatment group), age, children (number of children), college_deg (whether the participant has college degree or above), employed_now (if the participant is employed when conducting the experiment), employed_wife (if the participant’s wife is employed when conducting the experiment), num_know_per (percentage of people known in the session), num_mfs_per (percentage of people in the session with mutual friends), signed_up_number (whether the husband sign wife up for job matching), outside_wedge (guessing number of people in the session supporting WWOH minus the actual number of people in the session supporting WWOH).
+Variables will be used in the follow-up dataset are condition2 (control or treatment group), employed_3mos_out_fl (if the participant’s wife was employed three months ago when conducting the experiment), applied_out_fl (if the wife apply for job working outside), interviewed_out_fl (if the wife interview for job working outside), employed_now_out_fl (if the wife be employed for job outside), and driving_fl (if the husband is willing to sign his wife up for driving lessons).
+
 ### Online survey
@@
 Details and explanations using visualization will be further discusses in the next section.
+The variables will be used are c_outside_guess_frac (guessing the fraction that support WWOH in the control group), t_outside_guess_frac (guessing the fraction that support WWOH in the treatment group), c_outside_mean (the mean of actual proportion of support in the control group), t_outside_mean (the mean of actual proportion of support in the treatment group).
 
@@
 In the treatment group, where participants are given the actual proportion of support for WWOH, 32.02% of the respondents prefer to sign up their wives for the job service, which is a 32% increase (with a p-value of 0.0424).
-
 The combination of @tbl-summary_table and @fig-job_sign_up demonstrates the effects of the information intervention on participants’ behavior and opinions towards women's labor market participation, revealing not only a statistical significance but also practical importance in the context of social norms and labor supply outcomes in Saudi Arabia.
@@
 The longer-term outcomes of the experiment on information intervention are shown in @fig-3 with error bars indicating the 95% confidence intervals for these proportions.
-
 The percentage of wives applying for a job outside the home is presented in @fig-3 a.
@@
 Both @fig-3 a and @fig-3 b display significant increases.
-
 Regarding the employment rates for this kind of job, @fig-3 c shows that the employment rate increases from 7.69% to 9.73%.
@@
 The increase in husbands’ willingness to sign their wives up for driving lessons implies that correcting misperception influences beyond behaviours associated with female employment, creating potential impacts on broader social norms and attitudes toward women's conditions in Saudi Arabia.
-
 Overall, the treatment has a significant effects on both immediate and longer-term outcomes related to women labor market participation based on @fig-3.
@@
 Two vertical lines in @fig-national_survey_misperception represent the actual proportion of respondents who agree with the statement.
-
 There is no significant difference between the data concerning the control group and the treatment group.

### 2024-02-14 outputs/paper/paper.qmd
modify footnote

@@
 thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia.
-Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/"
+Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/.
+The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975."
 date: "February 12, 2024"
@@
 The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials.
-The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975
 

### 2024-02-14 outputs/paper/paper.qmd
improve the title

@@
 ---
-title: "Misperceived Social Norms about Women Working Outside the Home and Its Effect on Women in Saudi Arabia"
+title: "Misperceptions Regarding Women's Employment Outside the Home and Their Impact on Women in Saudi Arabia"
 author: 

### 2024-02-14 outputs/paper/paper.qmd
improve discussion

@@
 The prevailing societal norms in Saudi Arabia, characterized by a low rate of women working outside the home and the customary practice of husbands' guardianship with decision-making authority, contribute to the perception that Saudi men are unwilling to permit their wives to work [@MisperceivedSocialNorm].
-The paper ‘Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia’ by Leonardo Bursztyn, Alessandra L.
-González, and David Yanagizawa-Drott delves into this social norm, exploring Saudi men’s perceptions of opinions regarding WWOH.
+The paper ‘Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia’ by Bursztyn, González, and Yanagizawa-Drott delves into this social norm, exploring Saudi men’s perceptions of opinions regarding WWOH.
 
@@
 ## Inverse Pattern of Saudi female labor force participation rate during pandemic
-According to the Gender Data Portal from The World Bank, the global average male labor force participation had a decrease of 1.6%, reaching 58.6% in 2020, followed by a rebound to 59.5% in 2021.
+According to the Gender Data Portal from The World Bank, the global average labor force participation had a decrease of 1.6%, reaching 58.6% in 2020, followed by a rebound to 59.5% in 2021 [@worldbankLaborForce].
 In fact, this trend was observed across various countries, irrespective of gender.
-
 For example, the Canadian female labor force participation rates in 2019, 2020 and 2021 were 61.4%, 59.5%, 60.6%, respectively, and the Canadian male labor force participation rates for the same years were 70.1%, 68.6%, 69.6%.
-A similar pattern is discernible in India, where the female labor force participation rates in 2019, 2020 and 2021 were 23.7%, 22.7%, 23%, while corresponding male rates stood at 73.6%, 72.3%, 72.7% [@worldbankLaborForce].
+Similarly, the female labor force participation rates in 2019, 2020 and 2021 were 23.7%, 22.7%, 23%, while corresponding male rates stood at 73.6%, 72.3%, 72.7% in India [@worldbankLaborForce].
 
@@
 Moreover, the contrasting pattern in Saudi female labor force participation rate, compared to the world trend, highlights the phenomenon that many employed females tend to work at home, either willingly or due to traditional social norms.
-The 2020 surge could indicate potential willingness among Saudi women to explore employment opportunities.
+The surge observed in 2020 may suggest potential willingness among Saudi women to explore employment opportunities, which once again highlights the importance of correcting misperceptions.
 
@@
 
-In the original paper reveals that males who often engage in discussions about the WWOH have perceived proportion of support only four percent smaller than the actual proportion.
+Figure 9 in the original paper reveals that males who often engage in discussions about the WWOH have perceived proportion of support only four percent smaller than the actual proportion [@MisperceivedSocialNorm].
 For those who rarely or very rarely discuss about the WWOH, their perceived proportion of support for WWOH is around forty percent smaller than the actual proportion.
 If the lack of communication facilitates misperceptions, one would expect a correlation between the frequency of communication and perceptions [@MisperceivedSocialNorm].
-Consequently, future studies could delve into strategies in preventing misperceived opinions from influencing social norms negatively, and explore decision-making in the presence of collective misperceptions.
+Consequently, future studies could delve into strategies in preventing misperceived opinions from negatively influencing social norms, and explore decision-making in the presence of collective misperceptions.
 

### 2024-02-14 outputs/paper/paper.qmd
final improvement

@@
 abstract: "Husbands who hold guardianship and discourage their wives from working outside the home are often perceived as the main reason for the low female workforce participation in Saudi Arabia.
-We use data and surveys from the American Economic Association to analyze this perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men.
+This paper analyzes this common perception, revealing that a majority of young husbands in Saudi Arabia privately support women working outside the home but underestimate the support of other men.
 This paper also discusses the positive effects brought about by correcting this misperception, strategies for reducing information intervention, and the unusual Saudi female employment rate during the pandemic."
@@
 ## Source
-The paper used for replication is from American Economic Association, American Economic Review.
-The replication package is downloaded from Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia webpage, under Additional Materials.
-
-Our reproduction seeks to address two findings written in the original paper, using results they collected from the main experiment, its follow-up and online survey.
+The replication package is obtained from 'Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia', a paper from American Economic Association [@MisperceivedSocialNorm].
+Our reproduction seeks to address two findings written in the original paper, using results authors collected through the main experiment, follow-up, an online survey, and the programming language R [@r].
 

### 2024-02-14 scripts/00-simulation.R

@@ -24,9 +24,9 @@ library(knitr)
 set.seed(1232)
 condition <- c("0", "1")
 simulated_main_exp <-
-  tibble("Condition2" = sample(condition, 500, replace = TRUE),
-         "Age" = sample(18:35, 500, replace = TRUE),
-         "College_deg" = sample(0:1, 500, replace = TRUE),
+  tibble("condition2" = sample(condition, 500, replace = TRUE),
+         "age" = sample(18:35, 500, replace = TRUE),
+         "college_deg" = sample(0:1, 500, replace = TRUE),
          "employed_now" = sample(0:1, 500, replace = TRUE),
          "employed_wife" = sample(0:1, 500, replace = TRUE),
          "children" = sample(0:12, 500, replace = TRUE),
@@ -43,15 +43,16 @@ simulated_main_exp <-
          'signed_up_number' = sample(0:1, 500, replace = TRUE),
          'outside_guess' = sample(0:30, 500, replace = TRUE),
          'semiseg_guess' = sample(0:30, 500, replace = TRUE),
-         'mwage_guess' = sample(0:30, 500, replace = TRUE)) |> kable()
+         'mwage_guess' = sample(0:30, 500, replace = TRUE),
+         'outside_wedge' = sample(-29:29, 500, replace = TRUE))
 simulated_main_exp
 
 # Simulation for the follow-up
 simulated_follow_up <-
   tibble(
-    "Condition2" = sample(condition, 500, replace = TRUE),
-    "Age" = sample(18:35, 500, replace = TRUE),
-    "College_deg" = sample(0:1, 500, replace = TRUE),
+    "condition2" = sample(condition, 500, replace = TRUE),
+    "age" = sample(18:35, 500, replace = TRUE),
+    "college_deg" = sample(0:1, 500, replace = TRUE),
     "employed_now" = sample(0:1, 500, replace = TRUE),
     "employed_wife" = sample(0:1, 500, replace = TRUE),
     "children" = sample(0:12, 500, replace = TRUE),
@@ -63,28 +64,69 @@ simulated_follow_up <-
     'employed_3mos_out_fl' = sample(0:1, 500, replace = TRUE),
     'employed_now_out_fl' = sample(0:1, 500, replace = TRUE),
     'applied_out_fl' = sample(0:1, 500, replace = TRUE),
-    "interviewed_out_fl" = sample(0:1, 500, replace = TRUE),
[…]

### 2024-02-14 outputs/paper/paper.qmd
data cleaning is included now

@@
 Our reproduction seeks to address two findings written in the original paper, using results authors collected through the main experiment, follow-up, an online survey, and the programming language R [@r].
+
+## Data cleaning
+The raw dataset underwent a cleaning process to address missing values and recalibrate variables.
+This included updating the labor_demand_guess from multiple sources if it was missing, recalculating signed_up_number based on specific conditions, and removing out-of-range values from the age.
+New variables like college_deg and married were generated based on education and marital status, respectively.
+The dataset also saw the introduction of proportionate variables such as num_know_per and num_mfs_per.
+After refining variables for analysis, such as outside_guess, semiseg_guess, and mwage_guess, and their associated calculations, irrelevant variables were dropped.
+The cleaned data was then saved and is now ready for further analysis.
 

### 2024-02-15 outputs/paper/paper.qmd
finalize the paper and readme
final modification

@@
 thanks: "Code and data are available at: https://github.com/ScarletWu/Misperceived-Social-Norms-Women-Working-Outside-the-Home-in-Saudi-Arabia.
-Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/.
+Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1557/index?step=0.
 The original paper and its replicated package can be found here: https://www.aeaweb.org/articles?id=10.1257/aer.20180975."
@@
 ## Source
-The replication package is obtained from 'Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia', a paper from American Economic Association [@MisperceivedSocialNorm].
+The replication package is obtained from 'Misperceived Social Norms: Women Working Outside the Home in Saudi Arabia', a paper from the American Economic Association [@MisperceivedSocialNorm].
 Our reproduction seeks to address two findings written in the original paper, using results authors collected through the main experiment, follow-up, an online survey, and the programming language R [@r].

### 2024-02-15 outputs/paper/paper.qmd
final improvements

@@
 ### Main experiment and Follow-up
-The original study recruited 500 married Saudi males aged 18 to 35 from Riyadh as participants.
+The original study partnered with the local branch of an international survey company and recruited 500 married Saudi males aged 18 to 35 from Riyadh as participants.
 Initial contacts were established using a recruiter database, with further recruitment using a combination of snowball sampling and random street intercept [@MisperceivedSocialNorm].
@@
 Particularly, there were two statements about female labor participation.
-Following this, half of the participants were assigned to a treatment group randomly.
+Following this, half of the participants were assigned to a treatment group randomly by using the last three digits of their phone number.
 Those in the treatment group were provided with information on the proportion of respondents who agreed or disagreed with each statement, while participants in the control group received no information.
@@
 ### Online survey
-The online survey included approximately 1500 married Saudi men aged 18 to 35, randomly assigned to either a treatment or control group.
+The online survey included approximately 1500 married Saudi men aged 18 to 35, randomly assigned to either a treatment or control group, using the same platform and having the same layout as the original experiment.
 In the control group, participants were presented with statements that were contentious but not stigmatized.
